### 2024-11-29 paper/paper.qmd
update title and author

---
title: "Examining the Key Drivers of CAD/USD Exchange Rate: The Role of BCPI and Interest Rates in Canada's Economy"
subtitle: "My subtitle if needed"
author: 
  - Xinqi Yue
thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-11-29 scripts/03-clean_data.R
save analysis data in parquet format

@@ -10,6 +10,7 @@
 #### Workspace setup ####
 library(tidyverse)
 library(lubridate)
+library(arrow)
 
 #### Clean data ####
 weekly_bank_rate_data <- read_csv("data/01-raw_data/weekly_bank_rate_raw_data.csv")
@@ -72,4 +73,4 @@ cleaned_data <- cleaned_data |>
   )
 
 #### Save data ####
-write_csv(cleaned_data, "data/02-analysis_data/analysis_data.csv")
+write_parquet(cleaned_data, "data/02-analysis_data/analysis_data.parquet")

### 2024-11-29 scripts/04-test_analysis_data.R
change data test

@@ -20,8 +20,8 @@ analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
 head(analysis_data)
 
 # 3. Test that the dataset has the correct number of rows and columns
-test_that("dataset has 203 rows", {
-  expect_equal(nrow(analysis_data), 203)
+test_that("dataset has 204 rows", {
+  expect_equal(nrow(analysis_data), 204)
 })
 
 test_that("dataset has 6 columns", {  # Assuming there are 6 columns
@@ -64,8 +64,12 @@ test_that("'date' column contains valid dates", {
 })
 
 # 7. Test that there are no empty strings in any columns
-test_that("no empty strings in any column", {
-  expect_false(any(analysis_data == ""))
+test_that("no empty strings or NAs in any column", {
+  expect_true(all(!is.na(analysis_data$weekly_bank_rate) | analysis_data$weekly_bank_rate != ""))
+  expect_true(all(!is.na(analysis_data$weekly_avg_usd_vs_cad) | analysis_data$weekly_avg_usd_vs_cad != ""))
+  expect_true(all(!is.na(analysis_data$weekly_total_bcpi) | analysis_data$weekly_total_bcpi != ""))
+  expect_true(all(!is.na(analysis_data$weekly_energy_bcpi) | analysis_data$weekly_energy_bcpi != ""))
+  expect_true(all(!is.na(analysis_data$weekly_metel_bcpi) | analysis_data$weekly_metel_bcpi != ""))
 })
 
 # 8. Test that numeric columns contain only valid numeric values (no characters or invalid entries)

### 2024-11-29 paper/paper.qmd
add graphs, introduction and data section

@@
   - Xinqi Yue
-thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
+thanks: "Code and data are available at: https://github.com/xinqiyue/exchange-rate-analysis."
 date: today
@@
 #| message: false
+library(tidyverse)
+library(ggplot2)
+library(readr)
+library(gridExtra)
+library(arrow)
+```
 
-library(tidyverse)
-library(palmerpenguins)
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+analysis_data <- read_parquet("../data/02-analysis_data/analysis_data.parquet")
 ```
@@
 
-Overview paragraph
+## Overview
+The relationship between exchange rates, commodity prices, and interest rates is important in the economic dynamics of countries dependent on trade.
+For Canada, one of the world’s largest commodity producers, the exchange rate of the Canadian dollar (CAD) against the U.S.
+dollar (USD) is influenced by multiple factors, including global commodity prices and domestic interest rates.
+These variables not only affect Canada’s economic stability but also impact the broader global economy.
+Given Canada’s close trade ties with the United States, particularly in energy and metals, understanding the relationship between these factors is important for policymakers, traders, and economists alike.
 
-Estimand paragraph
+## Estimand
+This paper aims to estimate how the Bank of Canada Commodity Price Index (BCPI) and interest rates affect the CAD/USD exchange rate.
+The BCPI is categorized into various sub-indices, with particular focus on energy and metal BCPI, as these sectors represent key export areas for Canada.
+Linear regression analysis is used to examine the relationships between the CAD/USD exchange rate and the BCPI subcategories, as well as interest rates.
+The study seeks to determine the relative influence of these economic variables on the CAD/USD exchange rate.
 
-Results paragraph
+## Results
+The analysis finds a significant relationship between energy and metal prices, interest rates, and the CAD/USD exchange rate.
+Changes in energy and metal commodity prices, closely tied to Canada’s export performance, have a measurable effect on the value of the Canadian dollar relative to the U.S.
+dollar.
+These findings suggest that fluctuations in global commodity prices, particularly in energy and metals, play an important role in driving the CAD/USD exchange rate, with interest rates also contributing to these dynamics.
 
-Why it matters paragraph
+## Why it matters
+Understanding the factors that influence the CAD/USD exchange rate is important for Canadian policymakers, as well as traders and economists.
+Since Canada is heavily reliant on exports, particularly in the energy and metal sectors, shifts in the exchange rate can have wide-reaching implications for trade, inflation, and economic growth.
+By understanding the impact of BCPI subcategories on the exchange rate, Canadian policymakers can make more informed decisions regarding monetary policy and economic strategy, ensuring greater stability in trade relations with the U.S.
 
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+## Telegraphing
+The remainder of this paper is structured as follows: Section 2 reviews the relevant literature on exchange rates and commodity prices, Section 3 outlines the methodology used for the linear regression analysis, Section 4 presents the results and discusses their implications, and Section 5 concludes with policy recommendations and areas for future research.
 
@@
 ## Overview
+For this study, three primary data sets were used to explore the relationship between the Canadian dollar (CAD) and U.S.
+dollar (USD) exchange rate, commodity prices (via the Bank of Canada Commodity Price Index - BCPI), and interest rates.
+The data was collected from multiple publicly available sources: weekly exchange rates between the CAD and USD, weekly BCPI data from the Bank of Canada, and the Bank of Canada’s weekly interest rates.
+The exchange rate data set provides the value of the CAD against the USD, while the BCPI data set includes subcategories such as the total BCPI, energy BCPI, and metal BCPI.
+The interest rates data set provides the weekly bank rates set by the Bank of Canada.
 
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
-
-Overview text
+The data was processed and analyzed in R using several key R packages, including:
+- `readr` for reading CSV files,
+- `dplyr` for data manipulation and cleaning,
+- `ggplot2` for data visualization, and
+- `lm` (base R) for performing linear regression analysis.
 
 ## Measurement
+The data set used in this study includes variables related to exchange rates, bank rates, and the Bank of Canada Commodity Price Index (BCPI), which encompasses total, energy, and metal components.
+Below is a description of how these variables were measured and collected from their respective sources.
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+### Canadian Dollar (CAD) and U.S. Dollar (USD) Exchange Rates
+The exchange rate data was collected from the Bank of Canada's daily exchange rate series.
+These rates represent the average price at which one unit of U.S.
+dollars (USD) is exchanged for Canadian dollars (CAD), calculated from aggregated price quotes from financial institutions.
+In the data set, the exchange rates are represented as the number of Canadian dollars (CAD) per unit of U.S.
+dollars (USD).
+
+### Bank Rates
+The weekly Bank Rate was sourced from the Bank of Canada's official rates for monetary policy operations.
+The weekly Bank Rate represents the benchmark interest rate set by the Bank of Canada and is used as a reference for short-term inter bank loans.
+This data was gathered as part of the broader data set on Canadian interest rates and monetary policy variables.
+The values are expressed as a percentage (%).
+
+### Total BCPI
+The Total Bank of Canada Commodity Price Index (BCPI) represents the aggregated price of 26 commodities produced in Canada and traded globally.
+These commodities span sectors such as energy, metals and minerals, agriculture, forestry, and fisheries.
+The BCPI is calculated using the Chain Fisher price index methodology, which combines the advantages of both the Laspeyres and Paasche indices, providing a more accurate representation of price changes over time.
+This method uses the geometric mean of the price indices for successive periods, allowing for continuous updating of weights.
+The price movements of these commodities are measured in U.S.
+dollars, ensuring international comparability.
+The BCPI is computed using input-output (IO) tables by Statistics Canada, with the weights reflecting the relative importance of each commodity in Canada’s economy.
+The index values are published with a base year of 1972, where the index value is set to 100 for that year.
+
+### Energy BCPI
+The Energy BCPI includes the price movements of energy-related commodities such as crude oil, natural gas, and coal.
+The prices for these commodities are collected from a variety of sources, including the New York Mercantile Exchange (NYMEX) for oil and natural gas, and Kalibrate Canada Inc.
+for Western Canadian Select crude.
+The data is aggregated to form an index representing the overall price of energy commodities exported by Canada.
+The Energy BCPI is also measured in index points, with the same base year of 1972.
+
+### Metal BCPI
+The Metal BCPI includes the price movements of metals and minerals such as gold, silver, copper, and nickel.
+The prices for these commodities are collected from the London Metal Exchange (LME) and other sources, such as the Handy and Harman base price for gold and silver.
+These prices are used to construct an index representing the overall price changes in the metal commodities produced in Canada.
+Similar to the Energy BCPI, the Metal BCPI is measured in index points with the base year set to 1972.
+
+In summary, the measurement process involves collecting data from authoritative sources such as the Bank of Canada, the London Metal Exchange, and the New York Mercantile Exchange.
+The data is then processed into index points or percentage values to represent changes in exchange rates, interest rates, and commodity prices.
+The data is published on a regular basis with revisions made as new data becomes available.
+
+## Data cleaning
+
+*Variable Selection:* The analysis focused on the following key variables: Weekly Bank Rate, Weekly Total BCPI, Weekly Energy BCPI, Weekly Metal BCPI, and Weekly Average USD/CAD Exchange Rate.
+These were selected for their relevance to the research question and their potential influence on the exchange rate.
+
+*Missing and Empty Values*: Missing values and empty strings were identified and removed from the data sets both before and after merging.
+
+*Date and Data Type Conversion*: Dates were standardized to ensure consistency across datasets. The BCPI values were converted to numeric types, and any non-numeric data was removed.
+
+*Bank Rate Aggregation*: Daily bank_rate data was aggregated to weekly averages to match the temporal granularity of the other data sets.
+
+*Column Renaming*: Columns were renamed for clarity to improve readability and ensure consistency across datasets.
+
+*Data set Merging*: The data sets were merged by aligning the date column to create a unified data set.
 
 ## Outcome variables
-
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
-
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+### Weekly Average USD/CAD Exchange Rate
+This variable represents the average exchange rate of the Canadian dollar (CAD) against the U.S. dollar (USD) over each week. It captures the value of one USD in terms of CAD.
 
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
 #| echo: false
@@
 #| message: false
-
-analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
+#| fig-width: 12
+ggplot(analysis_data, aes(x = date, y = weekly_avg_usd_vs_cad)) +
+  geom_line(color = "#1f77b4", size = 1) +  # Line with custom color and size
+  labs(
+    title = "Trend of Weekly Average USD/CAD Exchange Rate",
+    x = "Year",
+    y = "USD/CAD Exchange Rate"
+  ) +
+  theme_minimal() +  # Clean and minimal theme
+  theme(
+    plot.title = element_text(size = 16, face = "bold"),
+    axis.title = element_text(size = 12),
+    axis.text = element_text(size = 10),
+    panel.grid.major = element_line(color = "gray90", size = 0.5),
+    panel.grid.minor = element_line(color = "gray95", size = 0.5)
+  ) +
+  scale_x_date(date_labels = "%Y", date_breaks = "1 year")  # Display only the year on the x-axis
 ```
-
-Talk way more about it.
 
@@
 
-Add graphs, tables and text.
+### Weekly Bank Rate
+#### Definition
+Represents the benchmark interest rate set by the Bank of Canada, typically used as a reference for short-term inter bank loans.
+This rate reflects the stance of monetary policy and plays a significant role in influencing exchange rates.
+- **Unit**: Percentage (%).
 
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-width: 12
+ggplot(analysis_data, aes(x = date, y = weekly_bank_rate)) +
+  geom_line(color = "#1f77b4", size = 1) +  # Line with custom color and size
+  labs(
+    title = "Weekly Bank Rate Over Time",
+    x = "Date",
+    y = "Weekly Bank Rate (%)"
+  ) +
+  theme_minimal() +
+  scale_x_date(
+    date_breaks = "1 year",  # Adjust to show one tick per year
+    date_labels = "%Y"  # Display the year
+  ) +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    axis.text.x = element_text(angle = 45, hjust = 1)
+  )
+
+```
+
+### Weekly Total BCPI
+#### Definition
+Represents the overall Bank of Canada Commodity Price Index (BCPI), which aggregates the prices of 26 key commodities produced in Canada and traded globally.
+The total BCPI reflects fluctuations in the overall price of Canadian export commodities, affecting export revenues and currency value.
+- **Unit**: Index Points (base year 1972 = 100).
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+# Plot 1: Weekly Total BCPI
+plot_bcpi <- ggplot(analysis_data) +
+  geom_line(aes(x = date, y = weekly_total_bcpi), color = "blue", size = 1) +
+  labs(
+    title = "Weekly Total BCPI",
+    x = "Date",
+    y = "BCPI"
+  ) +
+  scale_x_date(
+    date_breaks = "1 year",  # Show one tick per year
+    date_labels = "%Y"  # Format x-axis labels as years
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels to prevent overlap
+  )
+
+# Plot 2: Weekly Average USD/CAD Exchange Rate
+plot_usd_cad <- ggplot(analysis_data) +
+  geom_line(aes(x = date, y = weekly_avg_usd_vs_cad), color = "red", size = 1) +
+  labs(
+    title = "Weekly Average USD/CAD Exchange Rate",
+    x = "Date",
+    y = "USD/CAD"
+  ) +
+  scale_x_date(
+    date_breaks = "1 year",  # Show one tick per year
+    date_labels = "%Y"  # Format x-axis labels as years
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels to prevent overlap
+  )
+
+# Arrange the plots side by side
+grid.arrange(plot_bcpi, plot_usd_cad, nrow = 2)
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-width: 12
+# Normalize Weekly Total BCPI and Weekly Average USD/CAD Exchange Rate
+analysis_data <- analysis_data %>%
+  mutate(
+    normalized_bcpi = weekly_total_bcpi / max(weekly_total_bcpi, na.rm = TRUE),
+    normalized_usd_cad = weekly_avg_usd_vs_cad / max(weekly_avg_usd_vs_cad, na.rm = TRUE)
+  )
+
+# Plot normalized data
+ggplot(analysis_data) +
+  geom_line(aes(x = date, y = normalized_bcpi), color = "pink", size = 1, linetype = "solid") +
+  geom_line(aes(x = date, y = normalized_usd_cad), color = "black", size = 1, linetype = "solid") +
+  labs(
+    title = "Normalized Comparison of Weekly Total BCPI and Weekly Average USD/CAD Exchange Rate",
+    x = "Date",
+    y = "Normalized Values"
+  ) +
+  scale_x_date(
+    date_breaks = "1 year",  # Show one tick per year
+    date_labels = "%Y"  # Format x-axis labels as years
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels to prevent overlap
+    legend.position = "top"
+  ) +
+  scale_color_manual(
+    values = c("pink", "black"),
+    labels = c("Normalized Total BCPI", "Normalized USD/CAD Exchange Rate")
+  ) +
+  guides(color = guide_legend(title = "Variable"))
+
+```
+
+### Weekly Energy BCPI
+#### Definition
+Includes the price index of energy-related commodities such as crude oil, natural gas, and coal.
+Energy is one of the main sectors of Canada’s exports, and changes in energy prices may impact Canada’s economic performance and the strength of its currency.
+- **Unit**: Index Points (base year 1972 = 100).
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-width: 12
+# Normalize Weekly Total BCPI and Weekly Average USD/CAD Exchange Rate
+analysis_data <- analysis_data %>%
+  mutate(
+    normalized_energy_bcpi = weekly_energy_bcpi / max(weekly_energy_bcpi, na.rm = TRUE),
+    normalized_usd_cad = weekly_avg_usd_vs_cad / max(weekly_avg_usd_vs_cad, na.rm = TRUE)
+  )
+
+# Plot normalized data
+ggplot(analysis_data) +
+  geom_line(aes(x = date, y = normalized_energy_bcpi), color = "pink", size = 1, linetype = "solid") +
+  geom_line(aes(x = date, y = normalized_usd_cad), color = "black", size = 1, linetype = "solid") +
+  labs(
+    title = "Normalized Comparison of Weekly Energy BCPI and Weekly Average USD/CAD Exchange Rate",
+    x = "Date",
+    y = "Normalized Values"
+  ) +
+  scale_x_date(
+    date_breaks = "1 year",  # Show one tick per year
+    date_labels = "%Y"  # Format x-axis labels as years
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels to prevent overlap
+    legend.position = "top"
+  ) +
+  scale_color_manual(
+    values = c("pink", "black"),
+    labels = c("Normalized Energy BCPI", "Normalized USD/CAD Exchange Rate")
+  ) +
+  guides(color = guide_legend(title = "Variable"))
+
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-width: 12
+# Scatter plot: Weekly Energy BCPI vs Weekly Average USD/CAD Exchange Rate
+ggplot(analysis_data, aes(x = weekly_avg_usd_vs_cad, y = weekly_energy_bcpi)) +
+  geom_point(
+    color = "blue",        # Color of the points
+    size = 1,              # Size of the points
+    alpha = 0.6           # Transparency of the points
+  ) +
+  labs(
+    title = "Relationship Between Weekly Energy BCPI and USD/CAD Exchange Rate",
+    x = "Weekly Average USD/CAD Exchange Rate",
+    y = "Weekly Energy BCPI"
+  ) +
+  theme_minimal() +  # Clean theme
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 14),  # Center title and adjust size
+    axis.text.x = element_text(angle = 45, hjust = 1),   # Rotate x-axis labels for readability
+    axis.title = element_text(size = 12)                 # Larger axis titles
+  ) +
+  geom_smooth(method = "lm", se = FALSE, color = "red", size = 1) +  # Add linear regression line
+  scale_x_continuous(labels = scales::comma)  # Format x-axis to display commas for readability
+```
+
+### Weekly Metal BCPI
+#### Definition
+Includes the price index of metals and minerals such as gold, copper, nickel, and aluminum.
+These commodities are key components of Canada’s mining sector, and their price volatility may indirectly influence exchange rates.
+- **Unit**: Index Points (base year 1972 = 100).
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-width: 12
+# Normalize Weekly Total BCPI and Weekly Average USD/CAD Exchange Rate
+analysis_data <- analysis_data %>%
+  mutate(
+    normalized_metal_bcpi = weekly_metel_bcpi / max(weekly_metel_bcpi, na.rm = TRUE),
+    normalized_usd_cad = weekly_avg_usd_vs_cad / max(weekly_avg_usd_vs_cad, na.rm = TRUE)
+  )
+
+# Plot normalized data
+ggplot(analysis_data) +
+  geom_line(aes(x = date, y = normalized_metal_bcpi), color = "pink", size = 1, linetype = "solid") +
+  geom_line(aes(x = date, y = normalized_usd_cad), color = "black", size = 1, linetype = "solid") +
+  labs(
+    title = "Normalized Comparison of Weekly Metal BCPI and Weekly Average USD/CAD Exchange Rate",
+    x = "Date",
+    y = "Normalized Values"
+  ) +
+  scale_x_date(
+    date_breaks = "1 year",  # Show one tick per year
+    date_labels = "%Y"  # Format x-axis labels as years
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels to prevent overlap
+    legend.position = "top"
+  ) +
+  scale_color_manual(
+    values = c("pink", "black"),
+    labels = c("Normalized Metal BCPI", "Normalized USD/CAD Exchange Rate")
+  ) +
+  guides(color = guide_legend(title = "Variable"))
+
+```
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-width: 12
+# Scatter plot: Weekly Metal BCPI vs Weekly Average USD/CAD Exchange Rate
+ggplot(analysis_data, aes(x = weekly_avg_usd_vs_cad, y = weekly_metel_bcpi)) +
+  geom_point(
+    color = "blue",     # Color of the points
+    size = 1,                # Size of the points
+    alpha = 0.6              # Transparency of the points
+  ) +
+  labs(
+    title = "Relationship Between Weekly Metal BCPI and USD/CAD Exchange Rate",
+    x = "Weekly Average USD/CAD Exchange Rate",
+    y = "Weekly Metal BCPI"
+  ) +
+  theme_minimal() +  # Clean and minimal theme
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 14),  # Center the title and adjust size
+    axis.text.x = element_text(angle = 45, hjust = 1),   # Rotate x-axis labels for readability
+    axis.title = element_text(size = 12)                 # Larger axis titles for clarity
+  ) +
+  geom_smooth(method = "lm", se = FALSE, color = "red", size = 1) +  # Add a linear regression line
+  scale_x_continuous(labels = scales::comma)  # Format x-axis with commas for better readability
+
+```
+
+```{r}
+```
 
@@
 #| message: false
-
-library(rstanarm)
-
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
 ```
@@
 
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
-)
 ```
@@
 
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
+#pp_check(first_model) +
+#  theme_classic() +
+#  theme(legend.position = "bottom")
 
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
+#posterior_vs_prior(first_model) +
+#  theme_minimal() +
+#  scale_color_brewer(palette = "Set1") +
+#  theme(legend.position = "bottom") +
+#  coord_flip()
 ```
@@
 
-plot(first_model, "trace")
+#plot(first_model, "trace")
 
-plot(first_model, "rhat")
+#plot(first_model, "rhat")
 ```

### 2024-12-01 paper/paper.qmd
update paper (discussion, model, intro, data, reference)

--- 2024-11-29 paper/paper.qmd
@@
 ---
-title: "Examining the Key Drivers of CAD/USD Exchange Rate: The Role of BCPI and Interest Rates in Canada's Economy"
-subtitle: "My subtitle if needed"
+title: "Comparing the Impact of BCPI and Interest Rates on the CAD/USD Exchange Rate: A Model-Based Analysis of Key Drivers"
+subtitle: "Higher bank rates and commodity prices weaken the Canadian dollar, while rising energy prices strengthen it."
 author: 
   - Xinqi Yue
-thanks: "Code and data are available at: [https://github.com/RohanAlexander/starter_folder](https://github.com/RohanAlexander/starter_folder)."
+thanks: "Code and data are available at: https://github.com/xinqiyue/exchange-rate-analysis."
 date: today
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This study examines the factors influencing the USD/CAD exchange rate, focusing on the impact of Canadian bank rates and commodity prices.
+The analysis shows that higher bank rates and rising commodity prices, especially metal and total BCPI, are linked to a weaker Canadian dollar.
+In contrast, higher energy prices are associated with a stronger Canadian dollar.
+These findings are important for policymakers and investors as they help understand the key drivers of currency fluctuations and their broader economic effects."
 format: pdf
 number-sections: true
+toc: true
 bibliography: references.bib
@@
 #| message: false
-
 library(tidyverse)
-library(palmerpenguins)
+library(ggplot2)
+library(readr)
+library(gridExtra)
+library(arrow)
+library(car)
+library(kableExtra)
+library(modelsummary)
+library(knitr)
 ```
 
-# Introduction
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+analysis_data <- read_parquet("../data/02-analysis_data/analysis_data.parquet")
+model <- readRDS("../models/weekly_total_model.rds")
+model2 <- readRDS("../models/weekly_partial_model.rds")
+```
 
-Overview paragraph
+# Introduction {#sec-intro}
 
-Estimand paragraph
+## Overview
+The relationship between exchange rates, commodity prices, and interest rates is important in the economic dynamics of countries dependent on trade.
+For Canada, one of the world’s largest commodity producers, the exchange rate of the Canadian dollar (CAD) against the U.S.
+dollar (USD) is influenced by multiple factors, including global commodity prices and domestic interest rates.
+These variables not only affect Canada’s economic stability but also impact the broader global economy.
+Given Canada’s close trade ties with the United States, particularly in energy and metals, understanding the relationship between these factors is important for policymakers, traders, and economists alike.
 
-Results paragraph
+## Estimand
+The estimand of this analysis is the relationship between the USD/CAD exchange rate and four key predictors: the weekly bank rate, as well as the weekly BCPI indices (total, energy, and metal).
+The goal is to estimate how changes in the bank rate and fluctuations in global commodity prices, as captured by the BCPI, influence the value of the Canadian dollar relative to the U.S.
+dollar.
+Specifically, the analysis aims to quantify the effect of the bank rate on exchange rate movements and examine how the commodity prices (total, energy, and metal BCPI) contribute to the variability in the CAD/USD exchange rate.
 
-Why it matters paragraph
+## Results
+The analysis indicates that bank rates are positively associated with a depreciation of the Canadian dollar, which contradicts traditional economic theory.
+Commodity prices, particularly metal BCPI and total BCPI, are also positively related to a weaker Canadian dollar.
+However, energy BCPI shows a negative relationship with the exchange rate, suggesting that rising energy prices may help strengthen the Canadian dollar.
+Overall, higher bank rates and commodity prices are linked to a weaker Canadian dollar, with the effect of energy prices differing from other commodity indices.
 
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+## Why it matters
+Understanding the factors that influence the CAD/USD exchange rate is important for Canadian policymakers, as well as traders and economists.
+Since Canada is heavily reliant on exports, particularly in the energy and metal sectors, shifts in the exchange rate can have wide-reaching implications for trade, inflation, and economic growth.
+By understanding the impact of BCPI subcategories on the exchange rate, Canadian policymakers can make more informed decisions regarding monetary policy and economic strategy, ensuring greater stability in trade relations with the U.S.
+
+## Telegraphing
+The structure of this paper is as follows: @sec-intro provides an overview of the research topic and key objectives.
+In @sec-data, we outline the data sources and variables used for the analysis, including details on exchange rates, interest rates, and commodity price indices.
+The @sec-model section describes the model setup and justifications for selecting specific variables and methodologies.
+In @sec-result, we present the key findings of the regression analysis, including model performance and coefficient interpretations.
+The @sec-discussion section follows, where we explore the implications of the results, address potential limitations, and propose future research directions.
+Finally, @sec-appx offer additional details on the data, model diagnostics, and methodology used in the study.
+
+## Software
+This paper used R [@citeR] for data analysis, including data download and clean, regression diagnostics, model set up and summaries, and data visualization.
+
+- **data cleaning** The tidyverse package was used for efficient data manipulation and visualization (@tidyverse), lubridate was employed for handling date-time operations (@lubridate), and arrow facilitated reading and writing large data sets in parquet format (@arrow).
+
+- **visualization**: Ggplot2 [@ggplot2], gridExtra [@gridExtra], knitr[@knitr] and kableExtra [@kableExtra] packages to generate and optimize the graphs and tables in this analysis.
+
+- **model**: The car [@car] and modelsummary [@modelsummary] packages were used for regression diagnostics and model summaries.
 
@@
 ## Overview
-
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
-
-Overview text
+For this study, three primary data sets were used to explore the relationship between the Canadian dollar (CAD) and U.S.
+dollar (USD) exchange rate, commodity prices (via the Bank of Canada Commodity Price Index - BCPI), and interest rates.
+The data was collected from multiple publicly available sources: weekly exchange rates between the CAD and USD, weekly BCPI data from the Bank of Canada, and the Bank of Canada’s weekly interest rates.
+The exchange rate data set provides the value of the CAD against the USD [@bankofcanada_daily_exchange_rates], while the BCPI data set includes subcategories such as the total BCPI, energy BCPI, and metal BCPI [@bankofcanada_bcpi].
+The interest rates data set provides the weekly bank rates set by the Bank of Canada [@BankOfCanadaInterestRates].
+The BCPI is categorized into various types, with particular focus on energy and metal BCPI, as these sectors are main export areas for Canada.
 
 ## Measurement
+The data set used in this study includes variables related to exchange rates, bank rates, and the Bank of Canada Commodity Price Index (BCPI), which encompasses total, energy, and metal components.
+Below is a description of how these variables were measured and collected from their respective sources.
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+### Canadian Dollar (CAD) and U.S. Dollar (USD) Exchange Rates
+The exchange rate data was collected from the Bank of Canada's daily exchange rate series.
+These rates represent the average price at which one unit of U.S.
+dollars (USD) is exchanged for Canadian dollars (CAD), calculated from aggregated price quotes from financial institutions.
+In the data set, the exchange rates are represented as the number of Canadian dollars (CAD) per unit of U.S.
+dollars (USD).
+
+### Bank Rates
+The weekly Bank Rate was sourced from the Bank of Canada's official rates for monetary policy operations.
+The weekly Bank Rate represents the benchmark interest rate set by the Bank of Canada and is used as a reference for short-term inter bank loans.
+This data was gathered as part of the broader data set on Canadian interest rates and monetary policy variables.
+The values are expressed as a percentage (%).
+
+### Total BCPI
+The Total Bank of Canada Commodity Price Index (BCPI) represents the aggregated price of 26 commodities produced in Canada and traded globally.
+These commodities span sectors such as energy, metals and minerals, agriculture, forestry, and fisheries.
+The BCPI is calculated using the Chain Fisher price index methodology, which combines the advantages of both the Laspeyres and Paasche indices, providing a more accurate representation of price changes over time.
+This method uses the geometric mean of the price indices for successive periods, allowing for continuous updating of weights.
+The price movements of these commodities are measured in U.S.
+dollars, ensuring international comparability.
+The BCPI is computed using input-output (IO) tables by Statistics Canada, with the weights reflecting the relative importance of each commodity in Canada’s economy.
+The index values are published with a base year of 1972, where the index value is set to 100 for that year.
+
+### Energy BCPI
+The Energy BCPI includes the price movements of energy-related commodities such as crude oil, natural gas, and coal.
+The prices for these commodities are collected from a variety of sources, including the New York Mercantile Exchange (NYMEX) for oil and natural gas, and Kalibrate Canada Inc.
+for Western Canadian Select crude.
+The data is aggregated to form an index representing the overall price of energy commodities exported by Canada.
+The Energy BCPI is also measured in index points, with the same base year of 1972.
+
+### Metal BCPI
+The Metal BCPI includes the price movements of metals and minerals such as gold, silver, copper, and nickel.
+The prices for these commodities are collected from the London Metal Exchange (LME) and other sources, such as the Handy and Harman base price for gold and silver.
+These prices are used to construct an index representing the overall price changes in the metal commodities produced in Canada.
+Similar to the Energy BCPI, the Metal BCPI is measured in index points with the base year set to 1972.
+
+In summary, the measurement process involves collecting data from authoritative sources such as the Bank of Canada, the London Metal Exchange, and the New York Mercantile Exchange.
+The data is then processed into index points or percentage values to represent changes in exchange rates, interest rates, and commodity prices.
+The data is published on a regular basis with revisions made as new data becomes available.
+
+## Data cleaning
+
+*Variable Selection:* The analysis focused on the following key variables: Weekly Bank Rate, Weekly Total BCPI, Weekly Energy BCPI, Weekly Metal BCPI, and Weekly Average USD/CAD Exchange Rate.
+These were selected for their relevance to the research question and their potential influence on the exchange rate.
+
+*Missing and Empty Values*: Missing values and empty strings were identified and removed from the data sets both before and after merging.
+
+*Date and Data Type Conversion*: Dates were standardized to ensure consistency across datasets. The BCPI values were converted to numeric types, and any non-numeric data was removed.
+
+*Bank Rate Aggregation*: Daily bank_rate data was aggregated to weekly averages to match the temporal granularity of the other data sets.
+
+*Column Renaming*: Columns were renamed for clarity to improve readability and ensure consistency across datasets.
+
+*Data set Merging*: The data sets were merged by aligning the date column to create a unified data set.
 
 ## Outcome variables
+### Weekly Average USD/CAD Exchange Rate
+This variable represents the average exchange rate of the Canadian dollar (CAD) against the U.S. dollar (USD) over each week. It captures the value of one USD in terms of CAD.
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
-
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+@fig-exchange-rate-trend illustrates the fluctuations in the exchange rate between the U.S.
+dollar (USD) and the Canadian dollar (CAD) from January 1, 2021, to November 27, 2024.
+While the exchange rate experiences fluctuations, the overall trend shows an increase, indicating that the value of the Canadian dollar relative to the U.S.
+dollar has been weakening over this period.
+In other words, more Canadian dollars are needed to purchase one U.S.
+dollar as time progresses.
 
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
-```
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
-
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
 #| echo: false
@@
 #| message: false
-
-analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
-
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
+#| fig-width: 10
+#| label: fig-exchange-rate-trend
+#| fig-cap:  As time progresses, the amount of Canadian dollars (CAD) that can be exchanged for one U.S.
+dollar (USD) increases, indicating a overall decreasing trend in the value of the Canadian dollar relative to the U.S.
+dollar
+ggplot(analysis_data, aes(x = date, y = weekly_avg_usd_vs_cad)) +
+  geom_line(color = "#1f77b4", size = 1) +  # Line with custom color and size
+  labs(
+    title = "Trend of Weekly Average USD/CAD Exchange Rate",
+    x = "Year",
+    y = "USD/CAD Exchange Rate"
+  ) +
+  theme_minimal() +  # Clean and minimal theme
+  theme(
+    plot.title = element_text(size = 16, face = "bold"),
+    axis.title = element_text(size = 12),
+    axis.text = element_text(size = 10),
+    panel.grid.major = element_line(color = "gray90", size = 0.5),
+    panel.grid.minor = element_line(color = "gray95", size = 0.5)
+  ) +
+  scale_x_date(date_labels = "%Y", date_breaks = "1 year")  # Display only the year on the x-axis
 ```
-
-Talk way more about it.
 
@@
 
-Add graphs, tables and text.
+### Weekly Bank Rate
+Weekly Bank Rate represents the benchmark interest rate set by the Bank of Canada, typically used as a reference for short-term inter bank loans.
+This rate reflects the stance of monetary policy and plays a significant role in influencing exchange rates.
+- **Unit**: Percentage (%).
 
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
-
-# Model
-
-The goal of our modelling strategy is twofold. Firstly,...
-
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
-
-## Model set-up
-
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
-
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
-
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
-
-### Model justification
-
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
-# Results
-
-Our results are summarized in @tbl-modelresults.
+@fig-bank-rate-trend shows the trends in the weekly bank rate from January 2021 to November 2024.
+The rate steadily increased over time, reaching its highest level between mid-2023 and mid-2024.
+After this peak, the rate began to decrease, suggesting a shift in monetary policy or economic conditions that led to a reduction in the bank rate.
+The fluctuations reflect changes in the central bank's approach to managing the economy during this period.
 
@@
 #| echo: false
-#| eval: true
 #| warning: false
 #| message: false
+#| fig-width: 10
+#| fig-cap: Weekly bank rate from 2021 to November 2024, showing an overall increase with a peak in mid-2023 to mid-2024, followed by a decline.
+#| label: fig-bank-rate-trend
+ggplot(analysis_data, aes(x = date, y = weekly_bank_rate)) +
+  geom_line(color = "#1f77b4", size = 1) +  # Line with custom color and size
+  labs(
+    title = "Weekly Bank Rate Over Time",
+    x = "Date",
+    y = "Weekly Bank Rate (%)"
+  ) +
+  theme_minimal() +
+  scale_x_date(
+    date_breaks = "1 year",  # Adjust to show one tick per year
+    date_labels = "%Y"  # Display the year
+  ) +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    #axis.text.x = element_text(angle = 45, hjust = 1)
+  )
 
-library(rstanarm)
+```
 
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
+@fig-bank-agaist-exchange shows the relationship between the Weekly Bank Rate and the Weekly Average USD/CAD Exchange Rate.
+The data points show a positive trend, and the linear regression line suggests that as the weekly bank rate increases, the USD/CAD exchange rate also tends to rise.
+This indicates a positive correlation between the two variables.
+The upward slope of the regression line suggests that higher bank rates may have a tendency to push the exchange rate higher.
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-width: 10
+#| fig-cap: There is a positive relationship between the weekly bank rate and the USD/CAD exchange rate, with a linear regression line indicating upward trends.
+#| label: fig-bank-agaist-exchange
+# Scatter plot: Weekly Bank Rate vs Weekly Average USD/CAD Exchange Rate
+ggplot(analysis_data, aes(y = weekly_avg_usd_vs_cad, x = weekly_bank_rate)) +
+  geom_point(
+    color = "#ffb0bb",        # Color of the points
+    size = 1,              # Size of the points
+    alpha = 1.           # Transparency of the points
+  ) +
+  labs(
+    title = "Relationship Between Weekly Bank Rate and USD/CAD Exchange Rate",
+    y = "Weekly Average USD/CAD Exchange Rate",
+    x = "Weekly Bank Rate"
+  ) +
+  theme_minimal() +  # Clean theme
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 14),  # Center title and adjust size
+    #axis.text.x = element_text(angle = 45, hjust = 1),   # Rotate x-axis labels for readability
+    axis.title = element_text(size = 12)                 # Larger axis titles
+  ) +
+  geom_smooth(method = "lm", se = FALSE, color = "black", size = 1) +  # Add linear regression line
+  scale_x_continuous(labels = scales::comma)  # Format x-axis to display commas for readability
+```
+
+### Weekly Total BCPI
+Weekly Total BCPI represents the overall Bank of Canada Commodity Price Index (BCPI), which aggregates the prices of 26 key commodities produced in Canada and traded globally.
+The total BCPI reflects fluctuations in the overall price of Canadian export commodities, affecting export revenues and currency value.
+- **Unit**: Index Points (base year 1972 = 100).
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+#| fig-cap: Weekly Total BCPI and USD/CAD exchange rate trends over time, with BCPI peaking in mid-2022 and declining after that.
+# Plot 1: Weekly Total BCPI
+plot_bcpi <- ggplot(analysis_data) +
+  geom_line(aes(x = date, y = weekly_total_bcpi), color = "black", size = 1) +
+  labs(
+    title = "Weekly Total BCPI",
+    x = "Date",
+    y = "BCPI"
+  ) +
+  scale_x_date(
+    date_breaks = "1 year",  # Show one tick per year
+    date_labels = "%Y"  # Format x-axis labels as years
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels to prevent overlap
+  )
+
+# Plot 2: Weekly Average USD/CAD Exchange Rate
+plot_usd_cad <- ggplot(analysis_data) +
+  geom_line(aes(x = date, y = weekly_avg_usd_vs_cad), color = "pink", size = 1) +
+  labs(
+    title = "Weekly Average USD/CAD Exchange Rate",
+    x = "Date",
+    y = "USD/CAD"
+  ) +
+  scale_x_date(
+    date_breaks = "1 year",  # Show one tick per year
+    date_labels = "%Y"  # Format x-axis labels as years
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    axis.text.x = element_text(angle = 45, hjust = 1)  # Rotate x-axis labels to prevent overlap
+  )
+
+# Arrange the plots side by side
+grid.arrange(plot_bcpi, plot_usd_cad, nrow = 2)
+```
+
+@fig-total-bcpi-and-exchange presents a combined time-series plot of the Weekly Total BCPI and the Weekly Average USD/CAD Exchange Rate on the same timeline but with separate y-axes.
+The BCPI reaches its highest value around mid-2022 before experiencing a steady decline.
+Meanwhile, the USD/CAD exchange rate shows fluctuations throughout the observed period, with no apparent pattern that aligns with the BCPI's trends.
+This lack of correlation indicates that changes in the commodity price index do not directly correspond to movements in the exchange rate over time.
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-cap: Weekly Total BCPI and USD/CAD exchange rate trends over time, with BCPI peaking in mid-2022 and declining after that. No clear relationship between the two variables is observed.
+#| label: fig-total-bcpi-and-exchange
+#| fig-width: 8
+# Plot Weekly Total BCPI and Weekly Average USD/CAD Exchange Rate on one graph with dual y-axes
+ggplot(analysis_data, aes(x = date)) +
+  geom_line(aes(y = analysis_data$weekly_total_bcpi), color = "black", size = 1) +  # BCPI on the primary y-axis
+  geom_line(aes(y = analysis_data$weekly_avg_usd_vs_cad * max(analysis_data$weekly_total_bcpi, na.rm = TRUE) / 
+                   max(analysis_data$weekly_avg_usd_vs_cad, na.rm = TRUE)), 
+            color = "pink", size = 1) +  # USD/CAD scaled to match BCPI
+  scale_y_continuous(
+    name = "BCPI",  # Primary y-axis label
+    sec.axis = sec_axis(
+      ~ . * max(analysis_data$weekly_avg_usd_vs_cad, na.rm = TRUE) / max(analysis_data$weekly_total_bcpi, na.rm = TRUE), 
+      name = "USD/CAD Exchange Rate"  # Secondary y-axis label
+    )
+  ) +
+  labs(
+    title = "Weekly Total BCPI and USD/CAD Exchange Rate Trends",
+    x = "Date"
+  ) +
+  scale_x_date(
+    date_breaks = "1 year",  # Show one tick per year
+    date_labels = "%Y"  # Format x-axis labels as years
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    #axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels to prevent overlap
+    axis.title.y.left = element_text(color = "black"),  # Left y-axis color matches BCPI line
+    axis.title.y.right = element_text(color = "#ff909b")   # Right y-axis color matches USD/CAD line
+  )
 ```
@@
 #| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
 #| warning: false
+#| message: false
+#| fig-width: 10
+#| include: false
+# Normalize Weekly Total BCPI and Weekly Average USD/CAD Exchange Rate
+analysis_data <- analysis_data %>%
+  mutate(
+    normalized_bcpi = weekly_total_bcpi / max(weekly_total_bcpi, na.rm = TRUE),
+    normalized_usd_cad = weekly_avg_usd_vs_cad / max(weekly_avg_usd_vs_cad, na.rm = TRUE)
+  )
 
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
+# Plot normalized data
+ggplot(analysis_data) +
+  geom_line(aes(x = date, y = normalized_bcpi), color = "pink", size = 1, linetype = "solid") +
+  geom_line(aes(x = date, y = normalized_usd_cad), color = "black", size = 1, linetype = "solid") +
+  labs(
+    title = "Normalized Comparison of Weekly Total BCPI and Weekly Average USD/CAD Exchange Rate",
+    x = "Date",
+    y = "Normalized Values"
+  ) +
+  scale_x_date(
+    date_breaks = "1 year",  # Show one tick per year
+    date_labels = "%Y"  # Format x-axis labels as years
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels to prevent overlap
+    legend.position = "top"
+  ) +
+  scale_color_manual(
+    values = c("pink", "black"),
+    labels = c("Normalized Total BCPI", "Normalized USD/CAD Exchange Rate")
+  ) +
+  guides(color = guide_legend(title = "Variable"))
+```
+
+@fig-total-bcpi-scatter shows the relationship between the Weekly Total BCPI and the Weekly Average USD/CAD Exchange Rate.
+Each point represents an observed data point, with a linear regression line fitted to show the overall trend.
+The downward slope of the regression line indicates a negative relationship: as the Total BCPI increases, the USD/CAD exchange rate tends to decrease.
+This suggests that higher commodity prices might correspond to a stronger Canadian dollar (lower USD/CAD exchange rate).
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-width: 10
+#| fig-cap: Relationship between the Weekly Total BCPI and the USD/CAD exchange rate, showing a downward trend in the fitted line.
+#| label: fig-total-bcpi-scatter
+# Scatter plot: Weekly Total BCPI vs Weekly Average USD/CAD Exchange Rate
+ggplot(analysis_data, aes(y = weekly_avg_usd_vs_cad, x = weekly_total_bcpi)) +
+  geom_point(
+    color = "#ffb0bb",        # Color of the points
+    size = 1,              # Size of the points
+    alpha = 1.           # Transparency of the points
+  ) +
+  labs(
+    title = "Relationship Between Weekly Total BCPI and USD/CAD Exchange Rate",
+    y = "Weekly Average USD/CAD Exchange Rate",
+    x = "Weekly Total BCPI"
+  ) +
+  theme_minimal() +  # Clean theme
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 14),  # Center title and adjust size
+    axis.text.y = element_text(angle = 45, hjust = 1),   # Rotate x-axis labels for readability
+    axis.title = element_text(size = 12)                 # Larger axis titles
+  ) +
+  geom_smooth(method = "lm", se = FALSE, color = "black", size = 1) +  # Add linear regression line
+  scale_x_continuous(labels = scales::comma)  # Format x-axis to display commas for readability
+```
+
+### Weekly Energy BCPI
+Weekly Energy BCPI is defined as the price index of energy-related commodities such as crude oil, natural gas, and coal.
+Energy is one of the main sectors of Canada’s exports, and changes in energy prices may impact Canada’s economic performance and the strength of its currency.
+- **Unit**: Index Points (base year 1972 = 100).
+
+@fig-energy-bcpi-and-exchange presents a dual y-axis plot displaying the Weekly Energy BCPI and the Weekly Average USD/CAD Exchange Rate.
+The Energy BCPI reaches its highest value around mid-2022 and gradually declines after that, showing a trend similar to the Total BCPI.
+The USD/CAD exchange rate fluctuates throughout the period, but there is no apparent direct relationship between the exchange rate and the Energy BCPI.
+This suggests that the changes in the energy-related BCPI do not correlate with fluctuations in the USD/CAD exchange rate during the observed time.
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-cap: Weekly Energy BCPI and USD/CAD exchange rate trends over time, with Energy BCPI peaking in mid-2022 and declining after that. No clear relationship between the two variables is observed.
+#| label: fig-energy-bcpi-and-exchange
+#| fig-width: 8
+# Plot Weekly Energy BCPI and Weekly Average USD/CAD Exchange Rate on one graph with dual y-axes
+ggplot(analysis_data, aes(x = date)) +
+  geom_line(aes(y = analysis_data$weekly_energy_bcpi), color = "black", size = 1) +  # BCPI on the primary y-axis
+  geom_line(aes(y = analysis_data$weekly_avg_usd_vs_cad * max(analysis_data$weekly_energy_bcpi, na.rm = TRUE) / 
+                   max(analysis_data$weekly_avg_usd_vs_cad, na.rm = TRUE)), 
+            color = "pink", size = 1) +  # USD/CAD scaled to match BCPI
+  scale_y_continuous(
+    name = "Energy BCPI",  # Primary y-axis label
+    sec.axis = sec_axis(
+      ~ . * max(analysis_data$weekly_avg_usd_vs_cad, na.rm = TRUE) / max(analysis_data$weekly_energy_bcpi, na.rm = TRUE), 
+      name = "USD/CAD Exchange Rate"  # Secondary y-axis label
+    )
+  ) +
+  labs(
+    title = "Weekly Energy BCPI and USD/CAD Exchange Rate Trends",
+    x = "Date"
+  ) +
+  scale_x_date(
+    date_breaks = "1 year",  # Show one tick per year
+    date_labels = "%Y"  # Format x-axis labels as years
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    #axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels to prevent overlap
+    axis.title.y.left = element_text(color = "black"),  # Left y-axis color matches BCPI line
+    axis.title.y.right = element_text(color = "#ff909b")   # Right y-axis color matches USD/CAD line
   )
@@
 
-# Discussion
-
-## First discussion point {#sec-first-point}
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
-
-## Second discussion point
-
-Please don't use these as sub-heading labels - change them to be what your point actually is.
-
-## Third discussion point
-
-## Weaknesses and next steps
-
-Weaknesses and next steps should also be included.
-
-\newpage
-
-\appendix
-
-# Appendix {-}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+@fig-ener-exchange-scatter depicts the relationship between the Weekly Energy BCPI and the Weekly Average USD/CAD Exchange Rate.
+The regression line shows a slight negative slope, suggesting a weak inverse relationship between the two variables.
+As the Weekly Energy BCPI increases, the USD/CAD exchange rate tends to decrease slightly, though the correlation remains weak.
+Despite the visible trend, the scatter of data points indicates considerable variability, implying that other factors likely influence the exchange rate beyond the Energy BCPI.
 
 ```{r}
-#| eval: true
 #| echo: false
+#| warning: false
 #| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
+#| fig-width: 9
+#| fig-cap: Relationship between Weekly Energy BCPI and Weekly Average USD/CAD Exchange Rate.
+The scatter plot shows a slight negative correlation between the two variables, with the regression line indicating a slight downward slope.
+#| label: fig-ener-exchange-scatter
+# Scatter plot: Weekly Energy BCPI vs Weekly Average USD/CAD Exchange Rate
+ggplot(analysis_data, aes(y = weekly_avg_usd_vs_cad, x = weekly_energy_bcpi)) +
+  geom_point(
+    color = "#ffb0bb",        # Color of the points
+    size = 1,              # Size of the points
+    alpha = 1.           # Transparency of the points
+  ) +
+  labs(
+    title = "Relationship Between Weekly Energy BCPI and USD/CAD Exchange Rate",
+    y = "Weekly Average USD/CAD Exchange Rate",
+    x = "Weekly Energy BCPI"
+  ) +
+  theme_minimal() +  # Clean theme
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 14),  # Center title and adjust size
+   # axis.text.y = element_text(angle = 45, hjust = 1),   # Rotate x-axis labels for readability
+    axis.title = element_text(size = 12)                 # Larger axis titles
+  ) +
+  geom_smooth(method = "lm", se = FALSE, color = "black", size = 1) +  # Add linear regression line
+  scale_x_continuous(labels = scales::comma)  # Format x-axis to display commas for readability
 ```
 
-## Diagnostics
+### Weekly Metal BCPI
+Weekly Metal BCPI is the price index of metals and minerals such as gold, copper, nickel, and aluminum.
+These commodities are key components of Canada’s mining sector, and their price volatility may indirectly influence exchange rates.
+- **Unit**: Index Points (base year 1972 = 100).
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
+@fig-metal-bcpi-and-exchange illustrates the relationship between Weekly Metal BCPI and the USD/CAD exchange rate over time.
+The Metal BCPI shows a clear upward trend at the beginning, peaking in March 2023, and then decreasing.
+By February 2024, the index almost reaches its lowest point, similar to its level in January 2021, before beginning to rise again.
+The USD/CAD exchange rate is plotted on the secondary y-axis, but no strong correlation is observed between the two variables, suggesting that fluctuations in the Metal BCPI may directly align with movements in the exchange rate over this period.
 
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+```{r}
+#| label: fig-metal-bcpi-and-exchange
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-cap: The trends of Weekly Metal BCPI and the USD/CAD exchange rate, with the Metal BCPI showing an increase until peaking around March 2023, followed by a decline, almost reaching its lowest point in February 2024 before starting to rise again.
+No clear relationship between the two variables is observed from this graph.
+#| fig-width: 8
+
+# Plot Weekly Energy BCPI and Weekly Average USD/CAD Exchange Rate on one graph with dual y-axes
+ggplot(analysis_data, aes(x = date)) +
+  geom_line(aes(y = analysis_data$weekly_metal_bcpi), color = "black", size = 1) +  # BCPI on the primary y-axis
+  geom_line(aes(y = analysis_data$weekly_avg_usd_vs_cad * max(analysis_data$weekly_metal_bcpi, na.rm = TRUE) / 
+                   max(analysis_data$weekly_avg_usd_vs_cad, na.rm = TRUE)), 
+            color = "pink", size = 1) +  # USD/CAD scaled to match BCPI
+  scale_y_continuous(
+    name = "Metal BCPI",  # Primary y-axis label
+    sec.axis = sec_axis(
+      ~ . * max(analysis_data$weekly_avg_usd_vs_cad, na.rm = TRUE) / max(analysis_data$weekly_metal_bcpi, na.rm = TRUE), 
+      name = "USD/CAD Exchange Rate"  # Secondary y-axis label
+    )
+  ) +
+  labs(
+    title = "Weekly Metal BCPI and USD/CAD Exchange Rate Trends",
+    x = "Date"
+  ) +
+  scale_x_date(
+    date_breaks = "1 year",  # Show one tick per year
+    date_labels = "%Y"  # Format x-axis labels as years
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5),
+    #axis.text.x = element_text(angle = 45, hjust = 1),  # Rotate x-axis labels to prevent overlap
+    axis.title.y.left = element_text(color = "black"),  # Left y-axis color matches BCPI line
+    axis.title.y.right = element_text(color = "#ff909b")   # Right y-axis color matches USD/CAD line
+  )
+```
+
+@fig-metal-scatter shows the relationship between Weekly Metal BCPI and the USD/CAD exchange rate.
+A clear downward trend is observed, with the linear regression line sloping negatively.
+This suggests that as the Weekly Metal BCPI increases, the USD/CAD exchange rate tends to decrease.
+
+```{r}
+#| echo: false
+#| warning: false
+#| message: false
+#| fig-width: 10
+#| fig-cap: There us a negative relationship between Weekly Metal BCPI and the USD/CAD exchange rate, with a downward slope in the linear regression line indicating an inverse trend.
+#| label: fig-metal-scatter
+# Scatter plot: Weekly Metal BCPI vs Weekly Average USD/CAD Exchange Rate
+ggplot(analysis_data, aes(y = weekly_avg_usd_vs_cad, x = weekly_metal_bcpi)) +
+  geom_point(
+    color = "#ffb0bb",        # Color of the points
+    size = 1,              # Size of the points
+    alpha = 1.           # Transparency of the points
+  ) +
+  labs(
+    title = "Relationship Between Weekly Metal BCPI and USD/CAD Exchange Rate",
+    y = "Weekly Average USD/CAD Exchange Rate",
+    x = "Weekly Metal BCPI"
+  ) +
+  theme_minimal() +  # Clean and minimal theme
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 14),  # Center the title and adjust size
+    #axis.text.x = element_text(angle = 45, hjust = 1),   # Rotate x-axis labels for readability
+    axis.title = element_text(size = 12)                 # Larger axis titles for clarity
+  ) +
+  geom_smooth(method = "lm", se = FALSE, color = "black", size = 1) +  # Add a linear regression line
+  scale_x_continuous(labels = scales::comma)  # Format x-axis with commas for better readability
+
+```
+
+# Model {#sec-model}
+## Model Set-Up {#sec-modset}
+
+This analysis aims to predict the USD/CAD exchange rate using four key economic variables: bank rate, metal BCPI, energy BCPI, and total BCPI.
+We employ a multiple linear regression model to examine how these predictors relate to the exchange rate and identify the most significant drivers for currency fluctuations.
+
+We define the model as follows:
+
+$$
+\text{USD/CAD}_{t} = \beta_0 + \beta_1 \cdot \text{Bank Rate}_{t} + \beta_2 \cdot \text{Metal BCPI}_{t} + \beta_3 \cdot \text{Energy BCPI}_{t} + \epsilon_t
+$$
+
+$$
+\text{USD/CAD}_{t} = \beta_0 + \beta_1 \cdot \text{Bank Rate}_{t} + \beta_4 \cdot \text{Total BCPI}_{t} + \epsilon_t
+$$
+
+Where:
+
+- $\text{USD/CAD}_{t}$ is the predicted exchange rate at time $t$
+
+- $\beta_0$ is the intercept term
+
+- $\beta_1, \beta_2, \beta_3, \beta_4$ represent the coefficients for each predictor (bank rate, metal BCPI, energy BCPI, total BCPI)
+
+- $\epsilon_t$ is the error term at time $t$.
+
+This model quantifies the relationship between the exchange rate and the four predictors, allowing us to evaluate when the exchange rate is most favorable for converting Canadian dollars to U.S.
+dollars.
+
+## Model Justification
+
+We chose linear regression (LM) over models like GLM, Bayesian methods, and logistic regression for the following reasons:
+
+1.
+**Simplicity and Interpretability**: Linear regression is simple and its coefficients provide clear, direct interpretation of how predictors affect the dependent variable.
+More complex models would complicate this understanding.
+
+2.
+**Data Compatibility**: The response variable is continuous, making linear regression the best fit.
+GLM and logistic regression would not be suitable, as GLM requires assumptions about the error distribution and link functions, while logistic regression is for binary outcomes.
+
+3. **Computational Efficiency**: Linear regression is computationally efficient and quick to fit, whereas Bayesian and GLM approaches require more resources and time.
+
+4. **Assumption Fit**: Diagnostic tests confirmed that linear regression assumptions (linearity, homoscedasticity, normal residuals) were met, making it a good fit for the data set.
+
+Overall, linear regression is the most effective model for this analysis due to its simplicity, speed, and adequacy for continuous data.
+
+## Assumptions
+1.
+**Linearity**: We assume that the relationship between the predictors (bank rate, metal BCPI, energy BCPI, and total BCPI) and the dependent variable, the weekly USD/CAD exchange rate, is linear.
+From @fig-residuals-fitted, both models show no clear pattern, supporting the linearity assumption.
+
+2.
+**Independence of Errors**: The residuals in the model are assumed to be independent of one another.
+This means that there is no autocorrelation between consecutive residuals, which is a typical assumption in time series modeling.
+Violations of this assumption could indicate that the model has not captured some form of time dependency (e.g., lagged effects of one predictor on another), which may require adjustments such as the inclusion of lag terms or a more appropriate time-series model.
+From @fig-residuals-time, both models do not exhibit a discernible trend, suggesting that the independence assumption is satisfied.
+
+3.
+**Homoscedasticity**: The residuals ($\epsilon_t$) are assumed to be independent and identically distributed with constant variance (homoscedasticity).
+From @fig-residuals-fitted, we know the assumption is satisfied since the plot shows a random scatter of points with no discernible pattern, which indicates that the variance is constant.
+
+4.
+**No Multicollinearity**: The predictors used in the model are assumed not to be highly correlated with each other.
+High correlation between predictors can lead to multicollinearity, which can inflate the variance of the coefficient estimates and make it difficult to determine the individual effect of each predictor on the exchange rate.
+From @fig-vif1 and @fig-vif2, the Variance Inflation Factor (VIF) are low, which means the assumption is satisfied.
+
+5.
+**Normality of Residuals**: The residuals of the model are assumed to be normally distributed.
+From @fig-qq-plot, the QQ plot is approximately a straight line, which indicates that the assumption is satisfied for both of the model.
+
+## Limitations
+1. **Exclusion of Important Variables**: 
+The models only includes 4 predictors (bank rate, metal BCPI, energy BCPI, and total BCPI), omitting other relevant variables that could influence the USD/CAD exchange rate.
+Factors such as geopolitical events, inflation rates, oil prices, and global market sentiment may lead to fluctuations in currency but are not accounted for in the current model.
+This exclusion could limit the model’s ability to capture the full range of drivers influencing exchange rates.
+
+2. **Simplified Assumptions**: 
+The model assumes linear relationships between predictors and the dependent variable, which may not fully reflect the complexity of real-world exchange rate dynamics.
+Economic relationships can often be non-linear, and there may be interactions between predictors (e.g., the combined effects of bank rates and BCPI on exchange rates) that are not captured in this linear model.
+Further exploration of interaction terms or more complex modeling techniques (e.g., non-linear models) could provide a more accurate representation of the underlying dynamics.
+
+3. **Lack of Robustness to Structural Changes**: 
+Economic structures and market dynamics can change due to factors like policy shifts, technological advancements, or economic crises.
+This model may not be robust to such structural breaks, and its performance could deteriorate if significant changes in the economic environment occur.
+
+## Model Validation
+
+- **Out of Sample test**: To evaluate the models’ ability to generalize to unseen data, we performed out-of-sample testing by splitting the dataset into training (80%) and testing (20%) sets.
+From @fig-out-of-sample-test, the First Model, which includes weekly_bank_rate, weekly_metal_bcpi, and weekly_energy_bcpi, achieved an RMSE of 0.0231 and an MAE of 0.0168, outperforming the Second Model (which includes weekly_bank_rate and weekly_total_bcpi) with an RMSE of 0.0239 and an MAE of 0.0174.
+These results suggest that the First Model provides slightly better predictive accuracy by capturing the distinct effects of the BCPI components.
 
@@
 #| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
+#| label: fig-out-of-sample-test
+#| fig-cap: "Comparison of prediction performance between two regression models using RMSE and MAE metrics.
+The First Model, which includes bank rate, metal BCPI, and energy BCPI as predictors, performs slightly better (RMSE = 0.0231, MAE = 0.0168) than the Second Model, which includes bank rate and total BCPI (RMSE = 0.0239, MAE = 0.0174).
+This suggests that including disaggregated BCPI components may improve model accuracy."
+#| layout-ncol: 1
+# Split the dataset into training and testing sets
+set.seed(886) # Set the random seed to ensure reproducible results
+train_indices <- sample(1:nrow(analysis_data), size = 0.8 * nrow(analysis_data))
+train_data <- analysis_data[train_indices, ]
+test_data <- analysis_data[-train_indices, ]
 
-plot(first_model, "trace")
+# Fit the model on the training set
+model_train1 <- lm(weekly_avg_usd_vs_cad ~ weekly_bank_rate + weekly_metal_bcpi + weekly_energy_bcpi, data = train_data)
+model_train2 <- lm(weekly_avg_usd_vs_cad ~ weekly_bank_rate + weekly_total_bcpi, data = train_data)
 
-plot(first_model, "rhat")
+# Make predictions on the test set
+test_predictions1 <- predict(model_train1, newdata = test_data)
+test_predictions2 <- predict(model_train2, newdata = test_data)
+
+# Calculating RMSE and MAE
+rmse1 <- round(sqrt(mean((test_data$weekly_avg_usd_vs_cad - test_predictions1)^2)), 4)
+mae1 <- round(mean(abs(test_data$weekly_avg_usd_vs_cad - test_predictions1)), 4)
+
+rmse2 <- round(sqrt(mean((test_data$weekly_avg_usd_vs_cad - test_predictions2)^2)), 4)
+mae2 <- round(mean(abs(test_data$weekly_avg_usd_vs_cad - test_predictions2)), 4)
+
+# Creating tabular data
+results <- data.frame(
+  Model = c("First Model", "Second Model"),
+  RMSE = c(rmse1, rmse2),
+  MAE = c(mae1, mae2)
+)
+# Output results in table format
+results %>%
+    kbl(
+    #caption = "Summary statistics for key variables" #'Summary statistics for key variables',
+  ) %>%
+  kable_styling(
+    full_width = FALSE, position = "center",
+    latex_options = "scale_down"
+  ) %>%
+  kable_classic(full_width = FALSE, html_font = "Cambria")
+```
+
+- **Multicollinearity Check**: @fig-vif1 and @fig-vif2 shows low Variance Inflation Factor (VIF) values for all predictors in both models, ensuring that the variables are not highly correlated.
+This indicates that the coefficient estimates are stable and interpretable, allowing us to identify the individual contributions of predictors to the exchange rate.
+
+- **Model Summary**: From @tbl-modelresults, Both models demonstrated strong overall fit, with R² values of 0.831 and 0.824, respectively, and adjusted R² values slightly lower due to model complexity.
+The inclusion of additional predictors in the First Model results in slightly higher explanatory power.
+The Akaike Information Criterion (AIC) and Bayesian Information Criterion (BIC) also indicate that the First Model performs better despite its increased complexity.
+The residual standard errors are similar, reflecting consistent performance across both models.
+
+# Results {#sec-result}
+The primary objective of this analysis was to investigate the key drivers of the USD/CAD exchange rate, focusing on the influence of interest rates, metal BCPI, energy BCPI, and total BCPI.
+To achieve this, we developed two multiple linear regression models to predict the weekly exchange rate and assess the impact of these economic variables.
+
+## Model Performance
+Both models performed well in terms of predictive accuracy.
+By @fig-out-of-sample-test, the first model (which includes metal and energy BCPI) had an RMSE of 0.0231 and an MAE of 0.0168, while the second model (which includes total BCPI) showed an RMSE of 0.0239 and an MAE of 0.0174.
+Given that these values are relatively low and similar across both models, it indicates that the models are accurate in predicting the USD/CAD exchange rate, with only minor differences in performance.
+
+## Coefficients and Interpretation
+1.
+**Bank Rate**: By @tbl-modelresults, both models show a positive relationship between the **bank rate** and the exchange rate.
+In the first model, a 1% increase in the **bank rate** results in a 0.0241 increase in the exchange rate, and the second model shows a 0.0224 increase.
+This suggests that a higher **bank rate** tends to lead to a weaker Canadian dollar, as the exchange rate rises.
+This relationship is somewhat counterintuitive, as traditional economic theory suggests that higher interest rates should strengthen the currency.
+This observation will be further discussed in the @sec-discussion.
+
+2. **BCPI Components (Metal, Energy, and Total)**: From @tbl-modelresults, the coefficients for the BCPI components are quite small but still statistically significant:
+
+   - **Metal BCPI**: A 1-point increase in the **metal BCPI** results in a 0.0001 increase in the exchange rate.
+
+   - **Energy BCPI**: A 1-point increase in the **energy BCPI** leads to a decrease of 0.00002 in the exchange rate.
+
+   - **Total BCPI**: A 1-point increase in the **total BCPI** results in a 0.000003 increase in the exchange rate.
+
+Although the coefficients for BCPI components are relatively low, this could be attributed to the large range and average values of these indices as shown in @fig-data-sum.
+The **weekly energy BCPI** in particular has a broad span, with values ranging from 874.12 to over 2282.35.
+Thus, these results still indicate that commodity prices have a noticeable influence on the exchange rate.
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-modelresults
+#| tbl-cap: "Comparison of two regression models for the CAD/USD exchange rate.
+The weekly bank rate and metal BCPI have positive coefficients, indicating a depreciation effect on the Canadian dollar, while energy BCPI shows a negative coefficient, suggesting an appreciation effect.
+Total BCPI has minimal impact.
+Both models demonstrate strong explanatory power, with R² values above 0.82."
+#| warning: false
+modelsummary(list("First Model" = model, "Second Model" = model2), fmt = "%.6f")
+```
+
+# Discussion {#sec-discussion}
+
+This study aimed to investigate the factors influencing the USD/CAD exchange rate, with a particular focus on the role of interest rates and commodity prices, as measured by the Bank of Canada’s Commodity Price Index (BCPI).
+We used regression analysis to assess the relationship between the exchange rate and variables such as the bank rate, BCPI categories (total, energy, and metal).
+Based on the findings, this section will discuss the findings, limitations, and potential directions for future research.
+
+## Key Findings
+This paper explored the relationship between the **bank rate**, **commodity prices**, and the USD/CAD exchange rate.
+The results suggest that the **bank rate** and **commodity price indices** are significant factors influencing exchange rate fluctuations.
+Notably, the **bank rate** has a positive relationship with the USD/CAD exchange rate, indicating that higher rates are associated with a weaker Canadian dollar.
+This outcome is contrary to traditional economic theory, where we would expect higher interest rates to lead to a stronger currency.
+
+However, the observed results may be driven by complex underlying factors that were not captured by the model.
+Specifically, one potential explanation for this unexpected finding lies in **causal relationships**.
+In economic studies, it is often difficult to definitively establish the direction of causality between variables.
+Although theory suggests that higher interest rates should attract capital inflows and thus appreciate the domestic currency, in reality, it is possible that exchange rate fluctuations themselves may prompt adjustments in the **bank rate**.
+For example, the central bank might alter interest rates in response to exchange rate pressures to stabilize the economy.
+
+## Limitations
+
+- **Omitted Variables: ** One limitation of this study is the potential for **omitted variables** that could influence the USD/CAD exchange rate.
+For example, the analysis did not consider factors such as **economic growth**, **global political events**, or **international trade relations**, all of which can significantly affect the value of a currency.
+The exclusion of these factors might have led to an incomplete understanding of the exchange rate dynamics.
+
+- **Causality Issues: ** Another limitation arises from the difficulty of establishing clear **causal relationships** between the variables.
+While the model suggests that higher interest rates correlate with a weaker Canadian dollar, it is also possible that fluctuations in the exchange rate could influence the interest rate decisions, creating a **reverse causality**.
+For example, the Canadian central bank might adjust the bank rate in response to exchange rate pressures, rather than exchange rates reacting directly to changes in interest rates.
+
+- **Lag Effects: ** The model did not account for potential **lag effects** of interest rate changes on exchange rates.
+It is hard for monetary policy actions, such as changes in interest rates, to have an immediate impact on the economy and the exchange rate.
+The effects of interest rate adjustments might take several periods to materialize fully.
+Future models could consider the inclusion of lagged variables to capture these delayed effects.
+
+- **Economic Context: ** The study did not fully explore the broader macroeconomic context in which the exchange rate operates.
+Factors such as the fiscal policies, global economic conditions, and geopolitical events in USA could have significant impacts on the USA/CAD exchange rate but were not included in the model.
+These factors should be considered in future research to provide a more comprehensive understanding of exchange rate movements.
+
+## Future Research Directions
+
+- **Expanding the Model**: Future research could incorporate additional variables, such as economic growth, trade balances, and global economic indicators, to provide a more complete picture of the factors affecting the USD/CAD exchange rate.
+
+- **Causal Analysis**: Exploring the causal relationships between interest rates and exchange rates through more complex models (e.g., Granger causality tests or vector autoregression models) could provide clearer evidence on how these variables interact over time.
+
+- **Exploring Lagged Effects**: Incorporating lagged variables for interest rates and other key indicators could help better capture the delayed effects of monetary policy on exchange rates.
+
+- **Global Context**: Future studies could examine the effects of global economic conditions and geopolitical factors on the exchange rate, which would allow for a deeper understanding of the broader context in which the USD/CAD exchange rate is determined.
+
+\newpage
+
+\appendix
+
+# Appendix {#sec-appx}
+
+## Additional data details
+
+## Diagnostics
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-residuals-fitted
+#| fig-cap: "Residuals vs Fitted Values for the first (left) and second (right) models.
+The residuals are evenly distributed around zero, indicating no clear pattern, which supports the assumption of homoscedasticity (constant variance)."
+#| fig-width: 10
+par(mfrow = c(1, 2))
+plot(model$fitted.values, model$residuals,
+     xlab = "Fitted Values", ylab = "Residuals",
+     main = "Residuals vs Fitted Value (first model)")
+abline(h = 0, col = "red")
+
+plot(model2$fitted.values, model2$residuals,
+     xlab = "Fitted Values", ylab = "Residuals",
+     main = "Residuals vs Fitted Values (second model)")
+abline(h = 0, col = "red")
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-qq-plot
+#| fig-cap: "Normal Q-Q Plots for the first (left) and second (right) models. The points closely align with the diagonal line, supporting the assumption that residuals follow a normal distribution."
+#| fig-width: 10
+par(mfrow = c(1, 2))
+qqnorm(model$residuals)
+qqline(model$residuals, col = "red")
+qqnorm(model2$residuals)
+qqline(model2$residuals, col = "red")
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-residuals-time
+#| fig-cap: "Residuals vs Time for the first (left) and second (right) models.
+The residuals fluctuate randomly around zero over time, showing no clear trends, which supports the assumption of no autocorrelation in the residuals"
+#| fig-width: 10
+par(mfrow = c(1, 2))
+plot(1:length(model$residuals), model$residuals,
+     xlab = "Time", ylab = "Residuals", type = "l", main = "Residuals vs Time")
+abline(h = 0, col = "red")
+plot(1:length(model2$residuals), model2$residuals,
+     xlab = "Time", ylab = "Residuals", type = "l", main = "Residuals vs Time")
+abline(h = 0, col = "red")
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-vif1
+#| fig-cap: "Variance Inflation Factor (VIF) values for all predictors in the first models are below 5, indicating that multicollinearity is not a concern in these models."
+#| layout-ncol: 1
+vif_result <- vif(model)
+vif_result_df <- data.frame(vif_result)
+rownames(vif_result_df) <- c("weekly bank rate", "weekly metal BCPI", "weekly energy BCPI")
+
+vif_result_df <- round(vif_result_df, 3)
+vif_result_df %>%
+  kbl()# %>%
+  #kable_styling(latex_options = "scale_down")  # Adjust if needed
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-vif2
+#| fig-cap: "Variance Inflation Factor (VIF) values for all predictors in second models are below 5, indicating that multicollinearity is not a concern in these models."
+#| layout-ncol: 1
+vif_result2 <- vif(model2)
+vif_result_df2 <- data.frame(vif_result2)
+vif_result_df2 <- round(vif_result_df2, 3)
+rownames(vif_result_df2) <- c("weekly bank rate", "weekly total BCPI")
+vif_result_df2 %>%
+  kbl()
 ```
@@
 
+## Additional Tables & Graphs
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-data-sum
+#| fig-cap: "Summary statistics for key variables in the analysis, including weekly bank rate, USD/CAD exchange rate, and BCPI categories (total, energy, and metal), showing minimum, maximum, mean, and variance"
+# select variables
+selected_columns <- c("weekly_bank_rate", 
+                      "weekly_avg_usd_vs_cad", 
+                      "weekly_total_bcpi", 
+                      "weekly_energy_bcpi", 
+                      "weekly_metal_bcpi")
+# calculate min, max, mean, var
+summary_stats <- sapply(analysis_data[, selected_columns], function(x) {
+  c(min = min(x, na.rm = TRUE),
+    max = max(x, na.rm = TRUE),
+    mean = mean(x, na.rm = TRUE),
+    variance = var(x, na.rm = TRUE))
+})
+colnames(summary_stats) <- c("weekly bank rate", 
+                      "weekly average USD/CAD", 
+                      "weekly total BCPI", 
+                      "weekly energy BCPI", 
+                      "weekly metal BCPI")
+# Convert to data frame
+summary_stats_df <- as.data.frame(t(summary_stats))
+#summary_stats_df <- round(summary_stats_df, 2)
+summary_stats_df <- summary_stats_df %>% 
+  mutate(across(everything(), ~ formatC(.x, format = "f", big.mark = ",", digits = 2)))
+
+# Create the table and apply styling
+summary_stats_df %>%
+  kable() %>%
+  kable_styling(latex_options = "scale_down")  # Adjust if needed
+
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| fig-width: 8
+#| fig-cap: "Visualization of coefficient estimates and 95% confidence intervals from two regression models predicting the USD/CAD exchange rate.
+The weekly bank rate shows a consistent and significant positive impact, while the BCPI categories exhibit smaller effects.
+Energy BCPI has a slightly negative estimate, indicating a potential appreciating influence on the Canadian dollar, while metal BCPI has a small positive effect.
+Total BCPI demonstrates minimal influence."
+modelplot(list("First Model" = model, "Second Model" = model2), coef_map = c("weekly_bank_rate" = "Bank Rate", 
+                                            "weekly_metal_bcpi" = "Metal BCPI", 
+                                            "weekly_energy_bcpi" = "Energy BCPI", 
+                                            "weekly_total_bcpi" = "Total BCPI")) +
+  ggtitle("Coefficient Estimates for Predicting USD/CAD Exchange Rate") +
+  theme_minimal()
+```
+\newpage
+## Idealized Methodology
+
+## Idealized Survey
+
+\newpage
 # References

### 2024-12-01 scripts/03-clean_data.R
update scripts

@@ -48,7 +48,7 @@ weekly_BCPI_data <- weekly_BCPI_data |>
   filter(date > as.Date("2021-01-01")) |> # Filter rows after January 1, 2021
   rename(weekly_total_bcpi = w_bcpi, 
          weekly_energy_bcpi = w_ener, 
-         weekly_metel_bcpi = w_mtls)
+         weekly_metal_bcpi = w_mtls)
 
 # 4. Combine all datasets by date
 cleaned_data <- weekly_bank_rate_data |>
@@ -62,14 +62,14 @@ cleaned_data <- cleaned_data |>
 # Convert columns to numeric and remove rows with NA after conversion
 cleaned_data$weekly_total_bcpi <- as.numeric(cleaned_data$weekly_total_bcpi)
 cleaned_data$weekly_energy_bcpi <- as.numeric(cleaned_data$weekly_energy_bcpi)
-cleaned_data$weekly_metel_bcpi <- as.numeric(cleaned_data$weekly_metel_bcpi)
+cleaned_data$weekly_metal_bcpi <- as.numeric(cleaned_data$weekly_metal_bcpi)
 
 # Remove rows where any of the numeric columns are NA (after conversion)
 cleaned_data <- cleaned_data |> 
   filter(
     !is.na(weekly_total_bcpi) & 
       !is.na(weekly_energy_bcpi) & 
-      !is.na(weekly_metel_bcpi)
+      !is.na(weekly_metal_bcpi)
   )
 
 #### Save data ####

### 2024-12-01 scripts/04-test_analysis_data.R

@@ -49,8 +49,8 @@ test_that("'weekly_energy_bcpi' is numeric", {
   expect_type(analysis_data$weekly_energy_bcpi, "double")
 })
 
-test_that("'weekly_metel_bcpi' is numeric", {
-  expect_type(analysis_data$weekly_metel_bcpi, "double")
+test_that("'weekly_metal_bcpi' is numeric", {
+  expect_type(analysis_data$weekly_metal_bcpi, "double")
 })
 
 # 5. Test that there are no missing values in the dataset
@@ -69,7 +69,7 @@ test_that("no empty strings or NAs in any column", {
   expect_true(all(!is.na(analysis_data$weekly_avg_usd_vs_cad) | analysis_data$weekly_avg_usd_vs_cad != ""))
   expect_true(all(!is.na(analysis_data$weekly_total_bcpi) | analysis_data$weekly_total_bcpi != ""))
   expect_true(all(!is.na(analysis_data$weekly_energy_bcpi) | analysis_data$weekly_energy_bcpi != ""))
-  expect_true(all(!is.na(analysis_data$weekly_metel_bcpi) | analysis_data$weekly_metel_bcpi != ""))
+  expect_true(all(!is.na(analysis_data$weekly_metal_bcpi) | analysis_data$weekly_metal_bcpi != ""))
 })
 
 # 8. Test that numeric columns contain only valid numeric values (no characters or invalid entries)
@@ -78,7 +78,7 @@ test_that("numeric columns contain valid numeric values", {
   expect_true(all(is.numeric(analysis_data$weekly_avg_usd_vs_cad)))
   expect_true(all(is.numeric(analysis_data$weekly_total_bcpi)))
   expect_true(all(is.numeric(analysis_data$weekly_energy_bcpi)))
-  expect_true(all(is.numeric(analysis_data$weekly_metel_bcpi)))
+  expect_true(all(is.numeric(analysis_data$weekly_metal_bcpi)))
 })
 
 

### 2024-12-01 scripts/05-exploratory_data_analysis.R

@@ -13,7 +13,7 @@ library(tidyverse)
 library(rstanarm)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
 
 ### Model data ####
 first_model <-

### 2024-12-01 scripts/06-model_data.R

@@ -13,25 +13,44 @@ library(tidyverse)
 library(rstanarm)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 
 ### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+# Fit a linear regression model
+model <- lm(weekly_avg_usd_vs_cad ~ weekly_bank_rate + weekly_metal_bcpi + weekly_energy_bcpi, data = analysis_data)
+model2 <- lm(weekly_avg_usd_vs_cad ~ weekly_bank_rate + weekly_total_bcpi, data = analysis_data)
 
+set.seed(886) # 设置随机种子以确保结果可复现
+train_indices <- sample(1:nrow(analysis_data), size = 0.8 * nrow(analysis_data))
+train_data <- analysis_data[train_indices, ]
+test_data <- analysis_data[-train_indices, ]
 
-#### Save model ####
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
+# 在训练集上拟合模型
+model_train1 <- lm(weekly_avg_usd_vs_cad ~ weekly_bank_rate + weekly_metal_bcpi + weekly_energy_bcpi, data = train_data)
+model_train2 <- lm(weekly_avg_usd_vs_cad ~ weekly_bank_rate + weekly_total_bcpi, data = train_data)
+
+# 在测试集上进行预测
+test_predictions1 <- predict(model_train1, newdata = test_data)
+test_predictions2 <- predict(model_train2, newdata = test_data)
+
+# 计算RMSE和MAE
+rmse1 <- sqrt(mean((test_data$weekly_avg_usd_vs_cad - test_predictions1)^2))
+mae1 <- mean(abs(test_data$weekly_avg_usd_vs_cad - test_predictions1))
+
+rmse2 <- sqrt(mean((test_data$weekly_avg_usd_vs_cad - test_predictions2)^2))
[…]

### 2024-12-03 other/datasheet/datasheet_template.qmd
update paper and datasheet

---
title: "Datasheet for 'Commodity price index'"
subtitle: "the Bank of Canada commodity price index (BCPI)"
author: 
  - Xinqi Yue
thanks: "Code and data are available at: https://github.com/xinqiyue/exchange-rate-analysis.."
date: today
#date-format: "D MMMM YYYY"
#abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: ../../paper/references.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The Bank of Canada Commodity Price Index (BCPI) was created to support the Bank of Canada's analysis of commodity price movements and their impact on the Canadian economy, particularly in areas such as inflation, exchange rates, and economic growth. This dataset serves as a key input in the formulation of monetary policy by providing a comprehensive measure of commodity price trends relevant to Canada. The BCPI fills the gap in providing a standardized, weighted index of Canadian commodity prices denominated in USD, facilitating economic modeling and decision-making.

2. *Who created the data set (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The data set was created by the Bank of Canada, the nation's central bank. It was developed by the Bank's economic research and analysis team as part of its efforts to provide data for monitoring economic indicators and supporting monetary policy objectives.
3. *Who funded the creation of the data set? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - The creation of the data set was funded internally by the Bank of Canada. No external grants or funding sources are associated with this dataset, as it is developed and maintained as part of the Bank's regular operations.

**Composition**

1. *What do the instances that comprise the data set represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- The instances in the BCPI data set represent commodity price data for various goods produced in Canada and sold in global markets. These commodities are grouped into categories such as Energy, Metals and Minerals, Forestry, Agriculture, and Fisheries. Each instance in the data set corresponds to a specific commodity and its associated price data, which includes the commodity's price, its unit of measurement, and the date the price was recorded.

  - The data set can be thought of as containing multiple types of instances based on commodity categories (e.g., Energy, Metals, Agriculture) and the data points associated with each commodity (e.g., price, volume, or index). There are also temporal aspects involved, as the data includes weekly, monthly, and annual price records for each commodity.

2. *How many instances are there in total (of each type, if appropriate)?*
	- There are 26 commodities grouped into 5 main categories:
	- Energy: Includes coal, oil (three benchmarks), and natural gas.
	- Metals and Minerals: Includes gold, silver, nickel, copper, aluminum, zinc, potash, lead, and iron.
	- Forestry: Includes pulp, lumber, and newsprint.
	- Agriculture: Includes potatoes, cattle, hogs, wheat, barley, canola, and corn.
	- Fisheries: Includes finfish and shellfish.
	- This adds up to 26 individual commodities.
	- If using weekly data, the number of records per commodity equals the number of weeks in the dataset’s time span.
	- If using monthly data, the number of records per commodity equals the number of months in the time span.
	- For annual data, the number of records per commodity equals the number of years in the time span.

3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- **Larger Set**: The data set is a subset of global commodity transactions, focusing on 26 key commodities produced in Canada and priced in USD, relevant to Canada's export economy.

  - **Representativeness**: The data set is representative of Canadian commodities, selected based on economic significance and market relevance. Categories (e.g., energy, metals, agriculture) ensure broad sectoral coverage.

4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
- **Features**:

  - **Date**: The specific week of observation.

  - **Weekly Bank Rate**: Interest rates set by the Bank of Canada.

  - **Weekly Avg USD/CAD**: Average exchange rate of the Canadian Dollar against the US Dollar.

  - **Weekly Total BCPI**: Aggregated index for 26 key export commodities.

  - **Weekly Energy BCPI**: Sub-index focusing on energy-related commodities.

  - **Weekly Metals BCPI**: Sub-index for metals and minerals.

5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- No
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
  - the `raw_data` does not contain any missing values in its current form.  
  - The data has been curated and cleaned to ensure all required fields are present for analysis.  
  - The absence of missing values allows for direct analysis without the need for imputation or handling of gaps.

7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	The dataset includes temporal relationships between instances, as each row corresponds to a specific week.

8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- No

9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- **Errors**: No explicit errors have been identified in the data set. However, errors could arise from data entry inaccuracies or revisions in the source data.

  - **Sources of Noise**: Exchange rates and commodity prices may exhibit volatility due to market fluctuations, external shocks, or geopolitical events, introducing noise unrelated to the variables of interest.

  - **Redundancies**: The dataset does not appear to contain redundant rows or duplicate entries; each instance represents a unique weekly observation.

  - **Considerations**: Careful preprocessing, such as smoothing techniques or outlier detection, may help mitigate noise when analyzing trends or building models.

10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- The data set is **self-contained**, as it primarily consists of internal data collected from publicly available sources.

  - **External Dependencies**: The data on exchange rates and BCPI are sourced from external institutions like the Bank of Canada and financial platforms (e.g., market data services), but no continuous reliance on external resources is required for the data set itself.

11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- The data set **does not contain confidential data**.

  - It primarily includes **publicly available financial and economic data** such as the Bank of Canada Commodity Price Index (BCPI), exchange rates, and interest rates.

  - No personally identifiable information (PII), private communications, or data protected by legal privilege (such as doctor-patient confidentiality) is included in the data set.

12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- No.

13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- - Yes, the data set identifies sub-populations based on **industry sectors** within the BCPI.
- The BCPI is divided into multiple **sub-indices**, each representing a specific industry, including:
  - **Agriculture**
  - **Forestry**
  - **Energy**
  - **Metals and Minerals**
  - **Fisheries**

14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No, the data set does not contain information that directly or indirectly identifies individuals.

15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- No

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data was collected and reported by the Bank of Canada. It includes transaction prices for various commodities produced in Canada and sold in world markets. The prices are obtained from multiple sources such as futures markets, producer price indexes, and data from organizations like the New York Mercantile Exchange (NYMEX), London Metal Exchange (LME), and Statistics Canada.

2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- The data is collected through market transactions, official statistics, and publicly available price sources. The Bank of Canada compiles this data from various exchanges and other sources like Haver Analytics and Bloomberg L.P., and averages the daily or weekly prices for inclusion in the BCPI. Prices for commodities are either daily averages, weekly, or monthly data, depending on the commodity.

3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- The data set represents actual prices for a fixed set of commodities, collected and averaged across several periods (weekly, monthly, or annually). It is not a sample, but a full collection of available data for the commodities included in the BCPI, collected directly from relevant price sources.

4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- The data collection was performed by analysts and economists at the Bank of Canada. These individuals are responsible for gathering, processing, and updating the commodity price data. They also work with data sources like Statistics Canada, the National Energy Board, and other relevant agencies.

5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- The data is collected over multiple years, with updates available on a monthly, weekly, and annual basis. The timeframe includes long historical data series that are continuously updated, with regular revisions to reflect more accurate or newly available data.The earliest record is on 1972-01-12.

6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- The BCPI data set does not contain personal or sensitive information. Since it is composed of publicly available economic data (commodity prices) and compiled by a canadian central bank, ethical review processes are not required.

7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- The data was collected from third-party sources like futures exchanges (NYMEX, LME), commodity price reporting agencies (e.g., Haver Analytics, Bloomberg), and Statistics Canada. The Bank of Canada consolidates this data to generate the BCPI.

8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- There are no individuals involved in the dataset as it pertains to aggregate commodity prices. The dataset is purely economic in nature, with no personal data collection or individual notification needed.

9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- Consent is not applicable because the dataset does not involve personal data. The BCPI data is based on publicly available market data from recognized sources.

10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- Since there is no individual data or consent required, this is not applicable.

11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- As the dataset does not involve personal or sensitive data, there is no impact analysis or data protection impact assessment required. The dataset is used for economic modeling and analysis, which does not affect individuals directly.

12. *Any other comments?*
	- The BCPI dataset is an economic indicator used by government agencies, businesses, and researchers. Since it is based on publicly available market prices and does not involve personal information, the use of this dataset does not raise privacy concerns.

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- **Yes**, preprocessing and cleaning were done on the BCPI data. Some commodities have data available on different time intervals (e.g., daily, weekly, monthly), and the Bank of Canada averages prices over these intervals (daily, weekly, or monthly) for consistency in reporting. Missing values are typically handled by using the most recent available data until actual data is received. For instance, when data for a given period is not available, the most recent data is repeated, and this series is updated once the actual data becomes available. Additionally, the BCPI methodology is updated periodically, including adjustments to data from previous years, and corrections to commodity price sources like coal, barley, and lumber.

2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- No.

3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- The Bank of Canada does not explicitly provide software tools used for preprocessing or cleaning the BCPI data. However, the methodologies and algorithms used for weighting and aggregating data are outlined in their reports. The data processing procedures, such as using a chain Fisher price index and updating weights based on production volumes and price changes, are explained in the Bank of Canada's methodology documents. For more detailed insights into the methodology, you can refer to their official documentation: [BCPI Methodology](https://www.bankofcanada.ca/rates/price-indexes/bcpi/#methodology).

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- The Bank of Canada Commodity Price Index (BCPI) dataset has been used in various economic and financial analyses, particularly in studies examining the relationship between commodity prices and economic factors such as exchange rates, inflation, and trade balances.

	-Additionally, the BCPI data has been utilized for policy analysis, including understanding the effects of changes in commodity prices on Canada's monetary policy decisions. However, specific tasks and use cases for this dataset might vary depending on the research focus and analysis goals.

2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- The **Bank of Canada** provides access to the BCPI dataset through their official website, but it does not have a dedicated repository linking to all papers and systems that use the data.

3. *What (other) tasks could the dataset be used for?*
	- The BCPI dataset can be used for a variety of tasks, including:
     - **Predictive modeling**: Analyzing the relationship between commodity prices and exchange rates, interest rates, inflation, and economic growth.
     - **Market analysis**: Assessing the impact of commodity price fluctuations on Canadian industries, particularly those related to energy, agriculture, and natural resources.
     - **Policy analysis**: Supporting government decisions on monetary and fiscal policy by understanding the effects of commodity price changes on inflation and the trade balance.
     - **Risk management**: Analyzing potential risks in Canadian exports or in sectors highly dependent on commodity prices, such as energy and agriculture.
     - **Commodity price forecasting**: Developing models for predicting future commodity prices, which could inform investment strategies or policy recommendations.

4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- No.

5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- Microeconomic analysis of specific firms or sectors: The BCPI is a broad indicator of commodity prices and may not reflect the nuanced conditions of specific firms or sectors within Canada or globally.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	-  **Yes**, the BCPI dataset is publicly available through the **Bank of Canada** website and may be accessed by external parties for research and analytical purposes. The data is made available to various stakeholders, including researchers, policymakers, financial analysts, and the general public, to support economic and financial analysis.
	- For example, same dataset can be found on government of canada open data (https://open.canada.ca/data/en/dataset/d40af834-ae9c-43f2-82ea-57641910ac6f?_gl=1*76zq9g*_ga*MTI0MzQ4NTI1Ny4xNzMyNjU1NzQ2*_ga_S9JG8CZVYZ*MTczMzIwNjQxOS4yLjEuMTczMzIwNjQ4Ni42MC4wLjA.)

2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- The BCPI data set is distributed via the Bank of Canada website, where users can download it in formats such as CSV or Excel. It is not available through an API for automated access. As of now, the data set does not have a DOI, as it is provided by the Bank of Canada as a public resource rather than a formal academic data set.

3. *When will the dataset be distributed?*
	- The BCPI data set is updated regularly, with data typically released on a weekly, monthly or quarterly basis.

4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*

   - The BCPI data set is provided under the Bank of Canada’s Terms of Use. You are permitted to use, copy, and distribute the content freely, with the following conditions:
     - **Attribution**: You must credit the Bank of Canada as the source of the data and indicate if any changes were made.
     - **Accuracy**: You must ensure the accuracy of any content you reproduce.
     - **Notice Requirement**: If you incorporate the content into documents for sale, you must inform buyers that the content is freely available on the Bank of Canada website.

   The data set is provided at no cost for non-commercial use, and no additional fees apply. The full Terms of Use can be found here: [Bank of Canada Terms of Use](https://www.bankofcanada.ca/terms/).

5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- No

6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- The BCPI data set is not subject to export controls or regulatory restrictions. It is publicly available and can be used internationally without additional regulatory concerns. However, users should ensure compliance with any local laws or regulations when using the data outside of Canada. No specific supporting documentation for regulatory restrictions is required.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*

	- The dataset will be supported and maintained by the **Bank of Canada**, which is responsible for the collection, updating, and publication of the BCPI data. The Bank of Canada ensures the integrity and accuracy of the dataset as part of its role in supporting economic research and policy analysis.

2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- For inquiries related to the BCPI dataset, you can contact the Bank of Canada through the following options:
  - Use the online contact form available on the Bank of Canada Contact Page.(https://www.bankofcanada.ca/about/contact-information/general-inquiries/#online)
  - by phone: North America (Toll-Free): 1‑888‑882‑8863
  - by phone: Outside North America: +80078227800 (dial country code first)
  - Operating Hours: Monday to Friday, 7:00 to 17:00 (ET)

3. *Is there an erratum? If so, please provide a link or other access point.*
	- No.

4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- The dataset is updated regularly with new weekly data, but changes to past data will not be available in older versions. Updates are communicated via the Bank of Canada's website.

5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- Not applicable.

6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions will not be available once the data set is updated. However, new data will not affect previously recorded data, which remains accessible unless changes are made to historical data.

7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- No.

\newpage

# References

### 2024-12-03 paper/paper.qmd
update paper and datasheet

@@
 ---
-title: "Comparing the Impact of BCPI and Interest Rates on the CAD/USD Exchange Rate: A Model-Based Analysis of Key Drivers"
-subtitle: "Higher bank rates and commodity prices weaken the Canadian dollar, while rising energy prices strengthen it."
+title: "Modeling the Impact of Commodity Prices and Interest Rates on the CAD/USD Exchange Rate: An Analysis of Key Drivers Using Bank Rate and BCPI"
+subtitle: "Increase in bank rate, overall prices and metal prices weaken the Canadian dollar, while rising energy prices strengthen it."
 author: 
@@
 ## Idealized Methodology
-
-## Idealized Survey
-
+This study aims to analyze the impact of commodity prices, interest rates, and key economic events on the USD/CAD exchange rate.
+The current dataset, based on weekly data, has limitations, including an inability to capture short-term fluctuations and reliance on a single commodity price index (BCPI) that may not cover all relevant price movements.
+Additionally, the Bank of Canada’s bank rate is used as a proxy for interest rates, but it may not reflect other rates affecting investments, such as consumer or business loan rates.
+These limitations could affect the accuracy of the analysis.
+
+### Population and Sampling Approach
+
+The **target population** consists of all economic factors that influence the USD/CAD exchange rate, including commodity prices, interest rates, and exchange rates.
+The **sampling frame** will include data from international financial markets, central banks, and commodity markets, focusing on:
+
+- Commodity prices from various sectors (energy, metals, agriculture).
+
+- Interest rates from central banks and financial institutions.
+
+- Exchange rates from multiple financial sources.
+
+The **sampling frame** will include data sources such as central banks, commodity markets, financial institutions, and global news platforms.
+Data will be sampled across various time periods to capture long-term trends and short-term fluctuations.
+
+We will use a **stratified sampling** method to ensure that the data represent all key sectors, interest rates, and exchange rate sources. The focus will be on:
+- Price level: Different commodities (energy, metals, agriculture, etc.).
+- Interest rate: Various interest rate types (e.g., central bank rates, consumer and business loan rates).
+- Exchange rates: Real-time exchange rates from multiple financial institutions.
+
+### Data Collection and Measurement
+
+To address the limitations of the current dataset, the following improvements are proposed:
+
+1. **Higher-Frequency Data**:
+
+   - **Exchange Rates**: Daily exchange rate data for CAD/USD will be collected from financial platforms like Bloomberg, Reuters, and central banks (e.g., Bank of Canada).
+This will include rates from multiple institutions (e.g., commercial banks, currency exchanges).
+   - **Interest Rates**: Data on consumer loan rates, business loan rates, and global interest rates (e.g., U.S.
+Federal Reserve rates, European Central Bank rates) will be collected from central banks, commercial banks, and financial platforms.
+   **Variables Collected**:  
+   - **Exchange rates**: CAD/USD rates from multiple sources, such as commercial banks, forex markets, and central banks.
+   - **Interest rates**: Data on various types of interest rates: Bank of Canada’s overnight rate, U.S. Federal Reserve’s rate, consumer loan rates, business loan rates, and global bond yields.
+
+   **Advantage**: These data points will capture daily market fluctuations, allowing for a more granular view of interest rate and exchange rate dynamics.
+
+2. **Expanded Commodity Price Data**:  
+   - In addition to the BCPI, we will collect data from the **Global Commodity Price Index (GCPI)** and sector-specific indices (e.g., oil prices, natural gas, precious metals, and agricultural products).
+This will include daily or weekly prices from global commodity exchanges like the New York Mercantile Exchange (NYMEX) and London Metal Exchange (LME).
+
+   **Variables Collected**:  
+   - **Commodity prices**: Daily or weekly prices for energy commodities (oil, natural gas), metals (gold, silver, copper), and agricultural products (wheat, corn, soybeans).
+   - **Commodity index values**: GCPI and sector-specific price indices for comprehensive market coverage.
+
+   **Advantage**: This will provide a more accurate representation of how fluctuations in various commodity markets affect exchange rates.
+
+3. **Event-Driven Data**:  
+   - Major events, such as **U.S.
+presidential elections**, **trade policy changes**, and **commodity price shocks**, will be tracked.
+These events will be identified through news outlets, government reports, and financial news platforms.
+The impact of these events on the CAD/USD exchange rate will be measured by examining pre- and post-event exchange rate movements.
+
+   **Variables Collected**:  
+   - **Event indicators**: Data will include timestamps for events like U.S. elections, trade agreements, and major commodity price changes.
+   - **Exchange rate reactions**: Immediate changes in exchange rates before and after significant events.
+
+   **Advantage**: This will allow for direct analysis of how geopolitical and economic events affect currency markets.
+
+4. **Real-Time Data**:  
+   - Real-time exchange rates and interest rates will be obtained from financial platforms like Bloomberg, Reuters, and government releases.
+This will include high-frequency data (e.g., every minute or hourly data) to capture immediate market reactions to economic news and events.
+
+   **Variables Collected**:  
+   - **Real-time exchange rates**: CAD/USD exchange rate data collected from multiple financial institutions in real-time.
+   - **Real-time interest rates**: Instant updates on global interest rates, especially from major central banks and commercial financial entities.
+
+   **Advantage**: Real-time data will enable precise analysis of short-term fluctuations and market responses to economic news.
+
+### Conclusion
+
+The idealized methodology will improve upon the current dataset by incorporating higher-frequency data on exchange rates and interest rates, expanding commodity price coverage, and integrating event-driven data to assess the influence of global events.
+These improvements will address the limitations of the existing weekly data and provide a more detailed and accurate analysis of the factors driving the CAD/USD exchange rate.
+
+## Methodology Overview and Evaluation for BCPI data set
+
+The Bank of Canada Commodity Price Index (BCPI) uses a chain Fisher price index to track the transaction prices of 26 commodities produced in Canada and sold in global markets.
+These commodities cover a wide range of categories, including energy, metals, minerals, forestry, agriculture, and fisheries.
+The BCPI employs several data sources and methodologies to construct its index.
+
+### Data Collection and Processing Methodology
+The BCPI relies on data primarily from Statistics Canada’s input-output (IO) tables, with supplementary sources used when IO disaggregation is insufficient. The key methodology steps include:
+
+- **Commodity Prices**: The BCPI tracks spot or transaction prices in U.S.
+dollars for individual commodities.
+These prices are averaged over specific time periods (e.g., daily, weekly, monthly) to account for price fluctuations.
+
+- **Weighting**: The weight of each commodity in the index is derived from Canadian production values, which are adjusted over time using data from various sources such as the National Energy Board and Statistics Canada.
+The methodology incorporates changes in commodity prices and proxies for production volume.
+
+- **Projection of Weights**: The current methodology projects weights forward from the Input-Output reference year (2018) by approximating commodity value changes through commodity price adjustments and production volume proxies.
+Weights are reassessed four times a year to reflect the most recent price projections.
+
+- **Revisions and Adjustments**: The methodology also allows for historical revisions when more up-to-date data becomes available.
+For instance, the coal price series and some agricultural prices have undergone revisions in the past.
+
+### Strengths of the BCPI Methodology
+The BCPI methodology has several strengths:
+
+1. **Coverage**: By tracking a wide range of commodities, the BCPI provides an overview of Canadian market trends.
+
+2. **Regular Updates**: The BCPI supports weekly, quarterly and annually updates, ensuring that the weights and data reflect the short-term and long-term current price and production trends.
+
+3.
+**Use of Reliable Sources**: The index relies on reputable and recognized data sources, including Statistics Canada, the National Energy Board, and the New York Mercantile Exchange, enhancing the reliability and credibility.
+
+4.
+**Transparent Weighting Methodology**: The approach for determining commodity weights through production values and price proxies is transparent and well-documented, allowing users to understand how the index is constructed.
+
+### Limitations of the BCPI Methodology
+1.
+**Lag in Data Availability**: Since the index uses input-output tables that are updated with a lag, the most recent data may not always be included in the BCPI, potentially leading to outdated weights.
+
+2.
+**Dependence on Proxy Data**: For certain commodities, production volumes are estimated using proxies, which may not always fully capture the complexities of Canadian commodity production, especially in sectors with high variability or limited data.
+
+3.
+**Historical Data Revisions**: The revision of past data, such as changes to coal price series or shifts in the source of barley prices, could cause inconsistencies in historical comparisons, requiring caution when using the BCPI for longitudinal analysis.
+
+4.
+**Commodity Price Volatility**: The BCPI is sensitive to fluctuations in commodity prices, which can be influenced by a wide range of global factors.
+This volatility could lead to large swings in the index over short periods, making it challenging to capture long-term trends.
+
+Overall, the BCPI methodology provides useful information on Canadian pricing.
+However, its effectiveness may be impacted by data lags, the use of proxies for commodity production volumes, and periodic revisions..
 \newpage

### 2024-12-03 scripts/03-clean_data.R

@@ -46,6 +46,7 @@ weekly_BCPI_data <- weekly_BCPI_data |>
   tidyr::drop_na() |> # Remove rows with missing values
   mutate(date = ymd(date)) |> # Convert the date column to Date format
   filter(date > as.Date("2021-01-01")) |> # Filter rows after January 1, 2021
+  filter(date < as.Date("2024-12-01")) |>
   rename(weekly_total_bcpi = w_bcpi, 
          weekly_energy_bcpi = w_ener, 
          weekly_metal_bcpi = w_mtls)

### 2024-12-03 other/datasheet/datasheet_BCPI.qmd
delete unnecessary file and rename datasheet

--- 2024-12-03 other/datasheet/datasheet_template.qmd
@@
 date: today
-#date-format: "D MMMM YYYY"
-#abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
 format: pdf
@@
 7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
-	The dataset includes temporal relationships between instances, as each row corresponds to a specific week.
+	The data set includes temporal relationships between instances, as each row corresponds to a specific week.
 
@@
 9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
+
 	- **Errors**: No explicit errors have been identified in the data set. However, errors could arise from data entry inaccuracies or revisions in the source data.

### 2024-12-03 scripts/05-exploratory_data_analysis.R
delete unnecessary files

@@ -1,37 +1,0 @@
-#### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
-
-#### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
-
-#### Read data ####
-analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
-
-### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
-
-
-#### Save model ####
-saveRDS(
-  first_model,
-  file = "models/first_model.rds"
-)
-
-

### 2024-12-03 scripts/06-model_data.R

@@ -1,56 +1,0 @@
-#### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
-
-#### Workspace setup ####
-library(tidyverse)
-library(rstanarm)
-
-#### Read data ####
-analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
-
-### Model data ####
-# Fit a linear regression model
-model <- lm(weekly_avg_usd_vs_cad ~ weekly_bank_rate + weekly_metal_bcpi + weekly_energy_bcpi, data = analysis_data)
-model2 <- lm(weekly_avg_usd_vs_cad ~ weekly_bank_rate + weekly_total_bcpi, data = analysis_data)
-
-set.seed(886) # 设置随机种子以确保结果可复现
-train_indices <- sample(1:nrow(analysis_data), size = 0.8 * nrow(analysis_data))
-train_data <- analysis_data[train_indices, ]
-test_data <- analysis_data[-train_indices, ]
-
-# 在训练集上拟合模型
-model_train1 <- lm(weekly_avg_usd_vs_cad ~ weekly_bank_rate + weekly_metal_bcpi + weekly_energy_bcpi, data = train_data)
-model_train2 <- lm(weekly_avg_usd_vs_cad ~ weekly_bank_rate + weekly_total_bcpi, data = train_data)
-
-# 在测试集上进行预测
-test_predictions1 <- predict(model_train1, newdata = test_data)
-test_predictions2 <- predict(model_train2, newdata = test_data)
-
-# 计算RMSE和MAE
-rmse1 <- sqrt(mean((test_data$weekly_avg_usd_vs_cad - test_predictions1)^2))
-mae1 <- mean(abs(test_data$weekly_avg_usd_vs_cad - test_predictions1))
-
-rmse2 <- sqrt(mean((test_data$weekly_avg_usd_vs_cad - test_predictions2)^2))
-mae2 <- mean(abs(test_data$weekly_avg_usd_vs_cad - test_predictions2))
-
-# 创建表格数据
-results <- data.frame(
-  Model = c("First Model", "Second Model"),
[…]

### 2024-12-03 scripts/05-model_data.R
rename model script

@@ -1,0 +1,56 @@
+#### Preamble ####
+# Purpose: Models... [...UPDATE THIS...]
+# Author: Rohan Alexander [...UPDATE THIS...]
+# Date: 11 February 2023 [...UPDATE THIS...]
+# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# License: MIT
+# Pre-requisites: [...UPDATE THIS...]
+# Any other information needed? [...UPDATE THIS...]
+
+
+#### Workspace setup ####
+library(tidyverse)
+library(rstanarm)
+
+#### Read data ####
+analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
+
+### Model data ####
+# Fit a linear regression model
+model <- lm(weekly_avg_usd_vs_cad ~ weekly_bank_rate + weekly_metal_bcpi + weekly_energy_bcpi, data = analysis_data)
+model2 <- lm(weekly_avg_usd_vs_cad ~ weekly_bank_rate + weekly_total_bcpi, data = analysis_data)
+
+set.seed(886) # 设置随机种子以确保结果可复现
+train_indices <- sample(1:nrow(analysis_data), size = 0.8 * nrow(analysis_data))
+train_data <- analysis_data[train_indices, ]
+test_data <- analysis_data[-train_indices, ]
+
+# 在训练集上拟合模型
+model_train1 <- lm(weekly_avg_usd_vs_cad ~ weekly_bank_rate + weekly_metal_bcpi + weekly_energy_bcpi, data = train_data)
+model_train2 <- lm(weekly_avg_usd_vs_cad ~ weekly_bank_rate + weekly_total_bcpi, data = train_data)
+
+# 在测试集上进行预测
+test_predictions1 <- predict(model_train1, newdata = test_data)
+test_predictions2 <- predict(model_train2, newdata = test_data)
+
+# 计算RMSE和MAE
+rmse1 <- sqrt(mean((test_data$weekly_avg_usd_vs_cad - test_predictions1)^2))
+mae1 <- mean(abs(test_data$weekly_avg_usd_vs_cad - test_predictions1))
+
+rmse2 <- sqrt(mean((test_data$weekly_avg_usd_vs_cad - test_predictions2)^2))
+mae2 <- mean(abs(test_data$weekly_avg_usd_vs_cad - test_predictions2))
+
+# 创建表格数据
+results <- data.frame(
+  Model = c("First Model", "Second Model"),
[…]

### 2024-12-03 paper/paper.qmd
update preamble and correct paper typo

@@
 ## Overview
-For this study, three primary data sets were used to explore the relationship between the Canadian dollar (CAD) and U.S.
+For this study, three data sets were used to explore the relationship between the Canadian dollar (CAD) and U.S.
 dollar (USD) exchange rate, commodity prices (via the Bank of Canada Commodity Price Index - BCPI), and interest rates.
@@
 Overall, the BCPI methodology provides useful information on Canadian pricing.
-However, its effectiveness may be impacted by data lags, the use of proxies for commodity production volumes, and periodic revisions..
+However, its effectiveness may be impacted by data lags, the use of proxies for commodity production volumes, and periodic revisions.
 \newpage
+
 # References

### 2024-12-03 scripts/00-simulate_data.R

@@ -1,12 +1,13 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of Australian electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: simulates weekly economic data for USD/CAD exchange rates, 
+#           interest rates, BCPI, energy, and metals price indices over a 
+#           two-year period and saves it as a CSV file for further analysis.
+# Author: Xinqi Yue
+# Date: 3 Dec 2024
+# Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: The `tidyverse` package must be installed
-# Any other information needed? Make sure you are in the `starter_folder` rproj
+# Pre-requisites: The `tidyverse`, `dplyr`, `lubridate` and `tibble` package must be installed
+# Any other information needed? Make sure you are in the `exchange_rate_analysis` rproj
 
 
 #### Workspace setup ####

### 2024-12-03 scripts/01-test_simulated_data.R

@@ -1,15 +1,15 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: load and validate a simulated dataset, ensuring it meets specific 
+#          criteria such as correct number of rows and columns, no missing or 
+#          empty values, and that the date column is in weekly intervals.
+# Author: Xinqi Yue
+# Date: 3 Dec 2024
+# Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
-  # - The `tidyverse` package must be installed and loaded
-  # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
-
+#   - The `tidyverse` package must be installed
+#   - 00-simulate_data.R must have been run
+# Any other information needed? Make sure you are in the `exchange_rate_analysis` rproj
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-12-03 scripts/02-download_data.R

@@ -1,11 +1,12 @@
 #### Preamble ####
-# Purpose: Downloads and saves the data from [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Download the raw data sets.
+# Author: Xinqi Yue
+# Date: 3 Dec 2024
+# Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 
+#   - The `tidyverse` package must be installed
+# Any other information needed? Make sure you are in the `exchange_rate_analysis` rproj
 
 
 #### Workspace setup ####

### 2024-12-03 scripts/03-clean_data.R

@@ -1,11 +1,18 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: clean and preprocess three raw datasets (weekly bank rate data, 
+#         daily exchange rate data, and weekly BCPI data), by standardizing 
+#         column names, removing missing values, aggregating data where 
+#         necessary (e.g., converting daily exchange rates to weekly averages), 
+#         and merging the datasets into a single cleaned data frame. The final
+#         cleaned dataset is then saved in Parquet format for analysis.
+# Author: Xinqi Yue
+# Date: 3 Dec 2024
+# Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 
+#   - The `tidyverse`, `lubridate` and `arrow` package must be installed
+#   - 02-download_data.R must been run first
+# Any other information needed? Make sure you are in the `exchange_rate_analysis` rproj
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-12-03 scripts/04-test_analysis_data.R

@@ -1,11 +1,16 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: performs quality checks on the analysis_data dataset, ensuring 
+#         the correct number of rows and columns, proper data types, 
+#         no missing or empty values, and valid dates and numeric values.
+# Author: Xinqi Yue
+# Date: 3 Dec 2024
+# Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: 
+#   - The `tidyverse`, `testthat` and `dplyr` package must be installed
+#   - 02-download_data.R must been run first
+#   - 03-clean_data.R must been run Secondly
+# Any other information needed? Make sure you are in the `exchange_rate_analysis` rproj
 
 #### Workspace setup ####
 # Load necessary libraries

### 2024-12-03 scripts/05-model_data.R

@@ -1,16 +1,19 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose:  fits two linear regression models on the dataset, evaluates their 
+#         performance using RMSE and MAE on the test set, and saves the models 
+#         to disk for future use.
+# Author: Xinqi Yue
+# Date: 3 Dec 2024
+# Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
-
+# Pre-requisites: 
+#   - The `tidyverse` package must be installed
+#   - 02-download_data.R must been run first
+#   - 03-clean_data.R must been run Secondly
+# Any other information needed? Make sure you are in the `exchange_rate_analysis` rproj
 
 #### Workspace setup ####
 library(tidyverse)
-library(rstanarm)
 
 #### Read data ####
 analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
@@ -20,27 +23,27 @@ analysis_data <- read_parquet("data/02-analysis_data/analysis_data.parquet")
 model <- lm(weekly_avg_usd_vs_cad ~ weekly_bank_rate + weekly_metal_bcpi + weekly_energy_bcpi, data = analysis_data)
 model2 <- lm(weekly_avg_usd_vs_cad ~ weekly_bank_rate + weekly_total_bcpi, data = analysis_data)
 
-set.seed(886) # 设置随机种子以确保结果可复现
+set.seed(886) # Set the random seed to ensure reproducible results
 train_indices <- sample(1:nrow(analysis_data), size = 0.8 * nrow(analysis_data))
 train_data <- analysis_data[train_indices, ]
 test_data <- analysis_data[-train_indices, ]
 
-# 在训练集上拟合模型
+# Fit the model on the training set
 model_train1 <- lm(weekly_avg_usd_vs_cad ~ weekly_bank_rate + weekly_metal_bcpi + weekly_energy_bcpi, data = train_data)
[…]

### 2024-12-03 paper/paper.qmd
update (@) to [@]

@@
 
-- **data cleaning** The tidyverse package was used for efficient data manipulation and visualization (@tidyverse), lubridate was employed for handling date-time operations (@lubridate), and arrow facilitated reading and writing large data sets in parquet format (@arrow).
+- **data cleaning** The tidyverse package was used for efficient data manipulation and visualization [@tidyverse], lubridate was employed for handling date-time operations [@lubridate], and arrow facilitated reading and writing large data sets in parquet format [@arrow].
 

### 2024-12-03 scripts/00-simulate_data.R
update code style

@@ -1,6 +1,6 @@
 #### Preamble ####
-# Purpose: simulates weekly economic data for USD/CAD exchange rates, 
-#           interest rates, BCPI, energy, and metals price indices over a 
+# Purpose: simulates weekly economic data for USD/CAD exchange rates,
+#           interest rates, BCPI, energy, and metals price indices over a
 #           two-year period and saves it as a CSV file for further analysis.
 # Author: Xinqi Yue
 # Date: 3 Dec 2024
@@ -23,10 +23,10 @@ set.seed(687)
 # Set date range (weekly data)
 date_range <- seq.Date(from = as.Date("2022-01-01"), to = as.Date("2023-12-31"), by = "week")
 
-#Simulated exchange rate data (assuming fluctuations are between 1.2 and 1.4)
+# Simulated exchange rate data (assuming fluctuations are between 1.2 and 1.4)
 usd_cad_rate <- runif(length(date_range), min = 1.2, max = 1.4)
 
-#Simulated interest rate data (assumed to be between 0.5% and 3%)
+# Simulated interest rate data (assumed to be between 0.5% and 3%)
 interest_rate <- runif(length(date_range), min = 0.5, max = 3.0)
 
 # Simulate BCPI data (assumed to be between 90 and 110)

### 2024-12-03 scripts/01-test_simulated_data.R

@@ -1,12 +1,12 @@
 #### Preamble ####
-# Purpose: load and validate a simulated dataset, ensuring it meets specific 
-#          criteria such as correct number of rows and columns, no missing or 
+# Purpose: load and validate a simulated dataset, ensuring it meets specific
+#          criteria such as correct number of rows and columns, no missing or
 #          empty values, and that the date column is in weekly intervals.
 # Author: Xinqi Yue
 # Date: 3 Dec 2024
 # Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
+# Pre-requisites:
 #   - The `tidyverse` package must be installed
 #   - 00-simulate_data.R must have been run
 # Any other information needed? Make sure you are in the `exchange_rate_analysis` rproj
@@ -41,18 +41,30 @@ if (ncol(simulated_data) == 6) {
 }
 
 # Check if there are no empty strings or NA values in the relevant columns
-if (all(!is.na(simulated_data$Date) & simulated_data$Date != ""  # Check for missing values and empty strings in 'Date'
-        , na.rm = TRUE) &
-    all(!is.na(simulated_data$USD_CAD_Exchange_Rate) & simulated_data$USD_CAD_Exchange_Rate != ""  # 'USD_CAD_Exchange_Rate'
-        , na.rm = TRUE) &
-    all(!is.na(simulated_data$Interest_Rate) & simulated_data$Interest_Rate != ""  # 'Interest_Rate'
-        , na.rm = TRUE) &
-    all(!is.na(simulated_data$BCPI) & simulated_data$BCPI != ""  # 'BCPI'
-        , na.rm = TRUE) &
-    all(!is.na(simulated_data$Energy_Index) & simulated_data$Energy_Index != ""  # 'Energy_Index'
-        , na.rm = TRUE) &
-    all(!is.na(simulated_data$Metals_Index) & simulated_data$Metals_Index != ""  # 'Metals_Index'
-        , na.rm = TRUE)) {  # 'Metals_Index'
+if (all(!is.na(simulated_data$Date) & simulated_data$Date != "" # Check for missing values and empty strings in 'Date'
+  ,
+  na.rm = TRUE
+) &
[…]

### 2024-12-03 scripts/02-download_data.R

@@ -4,7 +4,7 @@
 # Date: 3 Dec 2024
 # Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
+# Pre-requisites:
 #   - The `tidyverse` package must be installed
 # Any other information needed? Make sure you are in the `exchange_rate_analysis` rproj
 
@@ -21,4 +21,3 @@ weekly_BCPI <- read_csv("https://www.bankofcanada.ca/valet/observations/group/BC
 write_csv(weekly_bank_rate, "data/01-raw_data/weekly_bank_rate_raw_data.csv")
 write_csv(daily_exchange_rate, "data/01-raw_data/daily_exchange_rate_raw_data.csv")
 write_csv(weekly_BCPI, "data/01-raw_data/weekly_BCPI_raw_data.csv")
-  

### 2024-12-03 scripts/03-clean_data.R

@@ -1,15 +1,15 @@
 #### Preamble ####
-# Purpose: clean and preprocess three raw datasets (weekly bank rate data, 
-#         daily exchange rate data, and weekly BCPI data), by standardizing 
-#         column names, removing missing values, aggregating data where 
-#         necessary (e.g., converting daily exchange rates to weekly averages), 
+# Purpose: clean and preprocess three raw datasets (weekly bank rate data,
+#         daily exchange rate data, and weekly BCPI data), by standardizing
+#         column names, removing missing values, aggregating data where
+#         necessary (e.g., converting daily exchange rates to weekly averages),
 #         and merging the datasets into a single cleaned data frame. The final
 #         cleaned dataset is then saved in Parquet format for analysis.
 # Author: Xinqi Yue
 # Date: 3 Dec 2024
 # Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
+# Pre-requisites:
 #   - The `tidyverse`, `lubridate` and `arrow` package must be installed
 #   - 02-download_data.R must been run first
 # Any other information needed? Make sure you are in the `exchange_rate_analysis` rproj
@@ -42,21 +42,23 @@ weekly_exchange_rate_data <- daily_exchange_rate_data |>
   mutate(
     date = date + days(3 - wday(date, week_start = 1)) # Group by week
   ) |>
-  group_by(date) |>  # Group by the new weekly column
+  group_by(date) |> # Group by the new weekly column
   summarise(weekly_avg_usd_vs_cad = mean(usd_vs_cad, na.rm = TRUE)) |> # Calculate weekly averages
   ungroup() # Ungroup to finalize the data frame
 
 # 3. Clean weekly_BCPI_data and select specific columns
-weekly_BCPI_data <- weekly_BCPI_data |> 
+weekly_BCPI_data <- weekly_BCPI_data |>
   janitor::clean_names() |> # Standardize column names
   select(date, w_bcpi, w_ener, w_mtls) |> # Keep only specified columns
   tidyr::drop_na() |> # Remove rows with missing values
   mutate(date = ymd(date)) |> # Convert the date column to Date format
   filter(date > as.Date("2021-01-01")) |> # Filter rows after January 1, 2021
[…]

### 2024-12-03 scripts/04-test_analysis_data.R

@@ -1,12 +1,12 @@
 #### Preamble ####
-# Purpose: performs quality checks on the analysis_data dataset, ensuring 
-#         the correct number of rows and columns, proper data types, 
+# Purpose: performs quality checks on the analysis_data dataset, ensuring
+#         the correct number of rows and columns, proper data types,
 #         no missing or empty values, and valid dates and numeric values.
 # Author: Xinqi Yue
 # Date: 3 Dec 2024
 # Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
+# Pre-requisites:
 #   - The `tidyverse`, `testthat` and `dplyr` package must be installed
 #   - 02-download_data.R must been run first
 #   - 03-clean_data.R must been run Secondly
@@ -29,7 +29,7 @@ test_that("dataset has 204 rows", {
   expect_equal(nrow(analysis_data), 204)
 })
 
-test_that("dataset has 6 columns", {  # Assuming there are 6 columns
+test_that("dataset has 6 columns", { # Assuming there are 6 columns
   expect_equal(ncol(analysis_data), 6)
 })
 
@@ -85,5 +85,3 @@ test_that("numeric columns contain valid numeric values", {
   expect_true(all(is.numeric(analysis_data$weekly_energy_bcpi)))
   expect_true(all(is.numeric(analysis_data$weekly_metal_bcpi)))
 })
-
-

### 2024-12-03 scripts/05-model_data.R

@@ -1,12 +1,12 @@
 #### Preamble ####
-# Purpose:  fits two linear regression models on the dataset, evaluates their 
-#         performance using RMSE and MAE on the test set, and saves the models 
+# Purpose:  fits two linear regression models on the dataset, evaluates their
+#         performance using RMSE and MAE on the test set, and saves the models
 #         to disk for future use.
 # Author: Xinqi Yue
 # Date: 3 Dec 2024
 # Contact: xinqi.yue@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: 
+# Pre-requisites:
 #   - The `tidyverse` package must be installed
 #   - 02-download_data.R must been run first
 #   - 03-clean_data.R must been run Secondly

### 2024-12-15 paper/paper.qmd
remove unnecesary words

@@
 These prices are used to construct an index representing the overall price changes in the metal commodities produced in Canada.
-Similar to the Energy BCPI, the Metal BCPI is measured in index points with the base year set to 1972.
+Like the Energy BCPI, the Metal BCPI is measured in index points with the base year set to 1972.
 
@@
 This indicates a positive correlation between the two variables.
-The upward slope of the regression line suggests that higher bank rates may have a tendency to push the exchange rate higher.
+The upward slope of the regression line suggests that higher bank rates may tend to push the exchange rate higher.
 
@@
 @fig-energy-bcpi-and-exchange presents a dual y-axis plot displaying the Weekly Energy BCPI and the Weekly Average USD/CAD Exchange Rate.
-The Energy BCPI reaches its highest value around mid-2022 and gradually declines after that, showing a trend similar to the Total BCPI.
+The Energy BCPI reaches its highest value around mid-2022 and gradually declines after that, showing a trend like the Total BCPI.
 The USD/CAD exchange rate fluctuates throughout the period, but there is no apparent direct relationship between the exchange rate and the Energy BCPI.
@@
 The Metal BCPI shows a clear upward trend at the beginning, peaking in March 2023, and then decreasing.
-By February 2024, the index almost reaches its lowest point, similar to its level in January 2021, before beginning to rise again.
+By February 2024, the index almost reaches its lowest point, like its level in January 2021, before beginning to rise again.
 The USD/CAD exchange rate is plotted on the secondary y-axis, but no strong correlation is observed between the two variables, suggesting that fluctuations in the Metal BCPI may directly align with movements in the exchange rate over this period.
@@
 **Normality of Residuals**: The residuals of the model are assumed to be normally distributed.
-From @fig-qq-plot, the QQ plot is approximately a straight line, which indicates that the assumption is satisfied for both of the model.
+From @fig-qq-plot, the QQ plot is approximately a straight line, which indicates that the assumption is satisfied for both models.
 
@@
 1. **Exclusion of Important Variables**: 
-The models only includes 4 predictors (bank rate, metal BCPI, energy BCPI, and total BCPI), omitting other relevant variables that could influence the USD/CAD exchange rate.
+The models only include 4 predictors (bank rate, metal BCPI, energy BCPI, and total BCPI), omitting other relevant variables that could influence the USD/CAD exchange rate.
 Factors such as geopolitical events, inflation rates, oil prices, and global market sentiment may lead to fluctuations in currency but are not accounted for in the current model.
@@
 Economic relationships can often be non-linear, and there may be interactions between predictors (e.g., the combined effects of bank rates and BCPI on exchange rates) that are not captured in this linear model.
-Further exploration of interaction terms or more complex modeling techniques (e.g., non-linear models) could provide a more accurate representation of the underlying dynamics.
+Further usage of interaction terms or more complex modeling techniques (e.g., non-linear models) could provide a more accurate representation of the underlying dynamics.
 
@@
 
-- **Model Summary**: From @tbl-modelresults, Both models demonstrated strong overall fit, with R² values of 0.831 and 0.824, respectively, and adjusted R² values slightly lower due to model complexity.
+- **Model Summary**: From @tbl-modelresults, both models demonstrated strong overall fit, with R² values of 0.831 and 0.824, respectively, and adjusted R² values slightly lower due to model complexity.
 The inclusion of additional predictors in the First Model results in slightly higher explanatory power.
@@
 Although the coefficients for BCPI components are relatively low, this could be attributed to the large range and average values of these indices as shown in @fig-data-sum.
-The **weekly energy BCPI** in particular has a broad span, with values ranging from 874.12 to over 2282.35.
+The **weekly energy BCPI** has a broad span, with values ranging from 874.12 to over 2282.35.
 Thus, these results still indicate that commodity prices have a noticeable influence on the exchange rate.
@@
 In economic studies, it is often difficult to definitively establish the direction of causality between variables.
-Although theory suggests that higher interest rates should attract capital inflows and thus appreciate the domestic currency, in reality, it is possible that exchange rate fluctuations themselves may prompt adjustments in the **bank rate**.
+Although theory suggests that higher interest rates should attract capital inflows and thus appreciate the domestic currency, it is possible that exchange rate fluctuations themselves may prompt adjustments in the **bank rate**.
 For example, the central bank might alter interest rates in response to exchange rate pressures to stabilize the economy.
@@
 Factors such as the fiscal policies, global economic conditions, and geopolitical events in USA could have significant impacts on the USA/CAD exchange rate but were not included in the model.
-These factors should be considered in future research to provide a more comprehensive understanding of exchange rate movements.
+These factors should be considered in future research to provide a better understanding of exchange rate movements.
 
@@
    - **Commodity prices**: Daily or weekly prices for energy commodities (oil, natural gas), metals (gold, silver, copper), and agricultural products (wheat, corn, soybeans).
-   - **Commodity index values**: GCPI and sector-specific price indices for comprehensive market coverage.
+   - **Commodity index values**: GCPI and sector-specific price indices for better market coverage.
 

### 2024-12-15 paper/paper.qmd
change typo

@@
 #| label: fig-vif1
-#| fig-cap: "Variance Inflation Factor (VIF) values for all predictors in the first models are below 5, indicating that multicollinearity is not a concern in these models."
+#| fig-cap: "Variance Inflation Factor (VIF) values for all predictors in the first model are below 5, indicating that multicollinearity is not a concern in these models."
 #| layout-ncol: 1
@@
 #| label: fig-vif2
-#| fig-cap: "Variance Inflation Factor (VIF) values for all predictors in second models are below 5, indicating that multicollinearity is not a concern in these models."
+#| fig-cap: "Variance Inflation Factor (VIF) values for all predictors in the second model are below 5, indicating that multicollinearity is not a concern in these models."
 #| layout-ncol: 1
